### 2018-12-10 paper/paper.tex
Skeleton of paper

\documentclass[a4paper,UKenglish]{lipics-v2018}
%This is a template for producing LIPIcs articles. 
%See lipics-manual.pdf for further information.
%for A4 paper format use option "a4paper", for US-letter use option "letterpaper"
%for british hyphenation rules use option "UKenglish", for american hyphenation rules use option "USenglish"
% for section-numbered lemmas etc., use "numberwithinsect"

\usepackage{microtype}%if unwanted, comment out or use option "draft"

%\graphicspath{{./graphics/}}%helpful if your graphic files are in another directory

\bibliographystyle{plainurl}% the recommnded bibstyle

\title{Guarded Recursive Type Theory via Sized Types}

\author{Niccol\`o Veltri}{Dummy University Computing Laboratory, [Address], Country}{johnqpublic@dummyuni.org}{https://orcid.org/0000-0002-1825-0097}{[funding]}%mandatory, please use full name; only 1 author per \author macro; first two parameters are mandatory, other parameters can be empty.

\author{Niels van der Weide}{iCIS, Radboud Universiteit, The Netherlands}{nweide@cs.ru.nl}{}{}

\authorrunning{J.\,Q. Public and J.\,R. Public}%mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et al.'

\Copyright{John Q. Public and Joan R. Public}%mandatory, please use full first names. LIPIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/

\subjclass{Dummy classification}% mandatory: Please choose ACM 2012 classifications from https://www.acm.org/publications/class-2012 or https://dl.acm.org/ccs/ccs_flat.cfm . E.g., cite as "General and reference $\rightarrow$ General literature" or \ccsdesc[100]{General and reference~General literature}.

\keywords{Dummy keyword}%mandatory

\category{}%optional, e.g. invited paper

\relatedversion{}%optional, e.g. full version hosted on arXiv, HAL, or other respository/website

\supplement{}%optional, e.g. related research data, source code, ... hosted on a repository like zenodo, figshare, GitHub, ...

\funding{}%optional, to capture a funding statement, which applies to all authors. Please enter author specific funding statements as fifth argument of the \author macro.

\acknowledgements{I want to thank \dots}%optional

%Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\EventEditors{John Q. Open and Joan R. Access}
\EventNoEds{2}
\EventLongTitle{42nd Conference on Very Important Topics (CVIT 2016)}
\EventShortTitle{CVIT 2016}
\EventAcronym{CVIT}
\EventYear{2016}
\EventDate{December 24--27, 2016}
\EventLocation{Little Whinging, United Kingdom}
\EventLogo{}
\SeriesVolume{42}
\ArticleNo{23}
%\nolinenumbers %uncomment to disable line numbering
%\hideLIPIcs  %uncomment to remove references to LIPIcs series (logo, DOI, ...), e.g. when preparing a pre-final version to be uploaded to arXiv or another public repository
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\maketitle

\begin{abstract}
Lorem ipsum dolor sit amet, consectetur adipiscing elit. Praesent convallis orci arcu, eu mollis dolor. Aliquam eleifend suscipit lacinia. Maecenas quam mi, porta ut lacinia sed, convallis ac dui. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Suspendisse potenti. 
 \end{abstract}

\section{Introduction}
\cite{atkey2013productive}

\section{Preliminaries}

\subsection{Sized Types}

\subsection{Guarded Recursive Type Theory}

\section{The Model}

\subsection{Clock Contexts}

\subsection{Presheaves}

\section{The Interpretation}

\subsection{Types, Contexts, Terms}

\subsection{Operations on Contexts}

\subsection{Substitution}

\subsection{Simple Types}

\subsection{Later}

\subsection{Clock Quantification}

\subsection{Fix}

\subsection{Inductive Types}

\section{Conclusion}

\appendix
\section{Omitted Proofs}

%%
%% Bibliography
%%

%% Please use bibtex,

\bibliography{literature}

\end{document}

### 2018-12-18 code-oneclock-paper/latex/paper.tex
Move to literate agda
Improvements in the code
Code in pdf (amsart)

--- 2018-12-10 paper/paper.tex
@@
-\documentclass[a4paper,UKenglish]{lipics-v2018}
+\documentclass{amsart}
+
+\usepackage{agda}
+
+% The following packages are needed because unicode
+% is translated (using the next set of packages) to
+% latex commands. You may need more packages if you
+% use more unicode characters:
+
+\usepackage{amssymb}
+\usepackage{bbm}
+
+% This handles the translation of unicode to latex:
+
+% Some characters that are not automatically defined
+% (you figure out by the latex compilation errors you get),
+% and you need to define:
+
+\DeclareUnicodeCharacter{931}{$\Sigma$}
+\DeclareUnicodeCharacter{948}{$\delta$}
+\DeclareUnicodeCharacter{957}{$\nu$}
+\DeclareUnicodeCharacter{8718}{$\blacksquare$}
+\DeclareUnicodeCharacter{8759}{::}
+\DeclareUnicodeCharacter{9659}{$\vartriangleright$}
+
+% Add more as you need them (shouldn't happen often).
+
+\newcommand{\AD}[1]{\AgdaDatatype{#1}}
+\newcommand{\AIC}[1]{\AgdaInductiveConstructor{#1}}
+\newcommand{\AF}[1]{\AgdaFunction{#1}}
+\newcommand{\AFi}[1]{\AgdaField{#1}}
+\newcommand{\AB}[1]{\AgdaBound{#1}}
+%\newcommand{\full}[1]{} %for the conference version
+\newcommand{\full}[1]{#1} % for the full version
+
 %This is a template for producing LIPIcs articles. 
@@
 \title{Guarded Recursive Type Theory via Sized Types}
-
-\author{Niccol\`o Veltri}{Dummy University Computing Laboratory, [Address], Country}{johnqpublic@dummyuni.org}{https://orcid.org/0000-0002-1825-0097}{[funding]}%mandatory, please use full name; only 1 author per \author macro; first two parameters are mandatory, other parameters can be empty.
-
-\author{Niels van der Weide}{iCIS, Radboud Universiteit, The Netherlands}{nweide@cs.ru.nl}{}{}
-
-\authorrunning{J.\,Q. Public and J.\,R. Public}%mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et al.'
-
-\Copyright{John Q. Public and Joan R. Public}%mandatory, please use full first names. LIPIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/
-
-\subjclass{Dummy classification}% mandatory: Please choose ACM 2012 classifications from https://www.acm.org/publications/class-2012 or https://dl.acm.org/ccs/ccs_flat.cfm .
-E.g., cite as "General and reference $\rightarrow$ General literature" or \ccsdesc[100]{General and reference~General literature}.
-
-\keywords{Dummy keyword}%mandatory
-
-\category{}%optional, e.g. invited paper
-
-\relatedversion{}%optional, e.g. full version hosted on arXiv, HAL, or other respository/website
-
-\supplement{}%optional, e.g. related research data, source code, ... hosted on a repository like zenodo, figshare, GitHub, ...
-
-\funding{}%optional, to capture a funding statement, which applies to all authors. Please enter author specific funding statements as fifth argument of the \author macro.
-
-\acknowledgements{I want to thank \dots}%optional
-
-%Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\EventEditors{John Q. Open and Joan R. Access}
-\EventNoEds{2}
-\EventLongTitle{42nd Conference on Very Important Topics (CVIT 2016)}
-\EventShortTitle{CVIT 2016}
-\EventAcronym{CVIT}
-\EventYear{2016}
-\EventDate{December 24--27, 2016}
-\EventLocation{Little Whinging, United Kingdom}
-\EventLogo{}
-\SeriesVolume{42}
-\ArticleNo{23}
-%\nolinenumbers %uncomment to disable line numbering
-%\hideLIPIcs  %uncomment to remove references to LIPIcs series (logo, DOI, ...), e.g. when preparing a pre-final version to be uploaded to arXiv or another public repository
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \section{Preliminaries}
+\input{Prelude/Basics}
+\input{Presheaves/Presheaves}
+\input{Presheaves/Const}
+\input{Presheaves/Terminal}
+\input{Presheaves/Product}
+\input{Presheaves/Sum}
+\input{Presheaves/Exp}
+\input{CloTT/Structure/Contexts}
+\input{CloTT/Structure/Types}
+\input{CloTT/Structure/Terms}
+\input{CloTT/Structure/DefinitionalEquality}
+\input{CloTT/Structure/ContextOperations}
+\input{CloTT/Structure/Subst}
+\input{CloTT/TypeFormers/UnitType}
+\input{CloTT/TypeFormers/SumType}
+\input{CloTT/TypeFormers/ProductType}
+\input{CloTT/TypeFormers/FunctionType}
+\input{CloTT/TypeFormers/ClockQuantification}
+\input{CloTT/TypeFormers/Later}
+\input{CloTT/TypeFormers/LaterType}
+\input{CloTT/TypeFormers/WeakenClock}
+\input{CloTT/TypeFormers/Fix}
+\input{CloTT/TypeFormers/Force}
 

### 2018-12-19 code-oneclock-paper/latex/paper.tex
experiments with literate Agda

@@
 
+\DeclareUnicodeCharacter{915}{$\Gamma$}
 \DeclareUnicodeCharacter{931}{$\Sigma$}
@@
 \newcommand{\full}[1]{#1} % for the full version
+
+% New commands for Agda inline code
+\newcommand{\D}{\AgdaDatatype}
+\newcommand{\IC}{\AgdaInductiveConstructor}
+\newcommand{\F}{\AgdaFunction}
+\newcommand{\Ar}{\AgdaArgument}
+\newcommand{\Fi}{\AgdaField}
 
@@
 \section{Preliminaries}
-\input{Prelude/Basics}
-\input{Presheaves/Presheaves}
-\input{Presheaves/Const}
-\input{Presheaves/Terminal}
-\input{Presheaves/Product}
-\input{Presheaves/Sum}
-\input{Presheaves/Exp}
-\input{CloTT/Structure/Contexts}
-\input{CloTT/Structure/Types}
-\input{CloTT/Structure/Terms}
-\input{CloTT/Structure/DefinitionalEquality}
-\input{CloTT/Structure/ContextOperations}
-\input{CloTT/Structure/Subst}
-\input{CloTT/TypeFormers/UnitType}
-\input{CloTT/TypeFormers/SumType}
-\input{CloTT/TypeFormers/ProductType}
-\input{CloTT/TypeFormers/FunctionType}
-\input{CloTT/TypeFormers/ClockQuantification}
-\input{CloTT/TypeFormers/Later}
-\input{CloTT/TypeFormers/LaterType}
-\input{CloTT/TypeFormers/WeakenClock}
-\input{CloTT/TypeFormers/Fix}
-\input{CloTT/TypeFormers/Force}
+%% \input{Prelude/Basics}
+%% \input{Presheaves/Presheaves}
+%% \input{Presheaves/Const}
+%% \input{Presheaves/Terminal}
+%% \input{Presheaves/Product}
+%% \input{Presheaves/Sum}
+%% \input{Presheaves/Exp}
+%% \input{CloTT/Structure/Contexts}
+%% \input{CloTT/Structure/Types}
+%% \input{CloTT/Structure/Terms}
+%% \input{CloTT/Structure/DefinitionalEquality}
+%% \input{CloTT/Structure/ContextOperations}
+%% \input{CloTT/Structure/Subst}
+%% \input{CloTT/TypeFormers/UnitType}
+%% \input{CloTT/TypeFormers/SumType}
+%% \input{CloTT/TypeFormers/ProductType}
+%% \input{CloTT/TypeFormers/FunctionType}
+%% \input{CloTT/TypeFormers/ClockQuantification}
+%% \input{CloTT/TypeFormers/Later}
+%% \input{CloTT/TypeFormers/LaterType}
+%% \input{CloTT/TypeFormers/WeakenClock}
+%% \input{CloTT/TypeFormers/Fix}
+%% \input{CloTT/TypeFormers/Force}
 
+%% \input{allcode}
 \subsection{Sized Types}
@@
 
+\section{Presheaves}
+
+A presheaf is a functor from the category of sizes to \D{Set}.
+
+\input{Presheaves/Presheaves}
+
+Every type \Ar{A} in \D{Set} defines a constant presheaf whose action
+on \Ar{i} is given by \Ar{A}, for any size \Ar{i}.
+\input{Presheaves/Const}
+
+Presheaves are the objects of a category whose morphisms are natural
+transformations. This is a cartesian closed category with finite
+coproducts.
+The terminal object is the constant presheaf on the unit type \D{⊤},
+i.e. \D{Terminal} = \D{Const ⊤}. Given two presheaves \Ar{P} and
+\Ar{Q}, we write \D{Prod} \Ar{P} \Ar{Q} for their cartesian
+product. The action of \D{Prod} \Ar{P} \Ar{Q} on a size \Ar{i} is
+defined as follows:
+\input{Presheaves/Product}
+%\Fi{PSh.Obj} \Ar{P i ×} \Fi{PSh.Obj} \Ar{Q i}.
+Coproducts are also defined in a similar pointwise way.
+
+Given two presheaves \Ar{P} and
+\Ar{Q}, we write \D{Exp} \Ar{P} \Ar{Q} for their exponential. 
+ The action of \D{Exp} \Ar{P} \Ar{Q} on a size \Ar{i} is
+defined as follows:
+\input{Presheaves/Exp}
+
 \section{The Model}
 
-\subsection{Clock Contexts}
+\subsection{Types, Contexts, Terms}
 
-\subsection{Presheaves}
+A context in \IC{set} is an element of \D{Set}. A context in \IC{tot}
+is a preasheaf in \D{PSh}.
 
-\section{The Interpretation}
+\input{CloTT/Structure/Contexts}
 
-\subsection{Types, Contexts, Terms}
+Since we are modeling a simply typed calculus, types are interpreted
+in the same ways as contexts.
+
+\input{CloTT/Structure/Types}
+
+In \IC{set}, a term of type \Ar{A} in context \Ar{Γ} is a function
+from \Ar{Γ} to \Ar{A}. In \IC{tot}, a term of type \Ar{A} in context
+\Ar{Γ} is a natural transformation between the presheaves \Ar{Γ} and
+\Ar{A}.
+
+\input{CloTT/Structure/Terms}
+
+Two types in \IC{set} are judgementally equal if and only if they are
+isomorphic as elements of \D{Set}. Two types in \IC{tot} are
+judgementally equal if and only if they are isomorphic as elements of
+\D{PSh}.
+
+Two terms in \IC{set} are judgementally equal if and only if they are
+propositionally equal as functions. Two terms in \IC{tot} are
+judgementally equal if and only if they are propositionally equal as
+natural transformations.
+
+\input{CloTT/Structure/DefinitionalEquality}
 
@@
 
+\section{The Interpretation}
+
 \section{Conclusion}

### 2019-01-07 code-oneclock-paper/latex/paper.tex
a bit of work on the paper on the plane
Fixed lipics and agda to latex

@@
-\documentclass{amsart}
+\documentclass[a4paper,UKenglish,cleveref, autoref,numberwithinsect]{lipics-v2018}
 
@@
 
+\usepackage{newunicodechar}
+
 % This handles the translation of unicode to latex:
@@
 
-\DeclareUnicodeCharacter{915}{$\Gamma$}
-\DeclareUnicodeCharacter{931}{$\Sigma$}
-\DeclareUnicodeCharacter{948}{$\delta$}
-\DeclareUnicodeCharacter{957}{$\nu$}
-\DeclareUnicodeCharacter{8718}{$\blacksquare$}
-\DeclareUnicodeCharacter{8759}{::}
-\DeclareUnicodeCharacter{9659}{$\vartriangleright$}
+\newunicodechar{⊤}{$\top$}
+\newunicodechar{≡}{$\equiv$}
+\newunicodechar{₁}{$_1$}
+\newunicodechar{Γ}{$\Gamma$}
+\newunicodechar{Σ}{$\Sigma$}
+\newunicodechar{λ}{$\lambda$}
+\newunicodechar{∙}{$\cdot$}
 
@@
 \newcommand{\Fi}{\AgdaField}
+
+\newcommand{\remove}[1]{}
 
@@
 \section{Presheaves}
-
 A presheaf is a functor from the category of sizes to \D{Set}.
@@
 defined as follows:
+\remove{
 \input{Presheaves/Product}
@@
 \input{Presheaves/Exp}
-
+}
 \section{The Model}
@@
 \subsection{Types, Contexts, Terms}
-
 A context in \IC{set} is an element of \D{Set}. A context in \IC{tot}
@@
 
-\subsection{Operations on Contexts}
-
-\subsection{Substitution}
+We write \D{∙} for the empty context and \Ar{Γ} \D{,,} \Ar{A} for the
+extension of the context \Ar{Γ} with the type \Ar{A}. We have
+the usual variable, weakening and substitutution operations.
+%\subsection{Operations on Contexts}
+%\subsection{Substitution}
 

### 2019-01-10 code-oneclock-paper/latex/paper.tex
All the code

@@
 \usepackage{newunicodechar}
+\usepackage{stmaryrd}
 
@@
 \newunicodechar{₁}{$_1$}
+\newunicodechar{₂}{$_2$}
 \newunicodechar{Γ}{$\Gamma$}
+\newunicodechar{Δ}{$\Delta$}
 \newunicodechar{Σ}{$\Sigma$}
+\newunicodechar{α}{$\alpha$}
+\newunicodechar{γ}{$\gamma$}
+\newunicodechar{ε}{$\varepsilon$}
 \newunicodechar{λ}{$\lambda$}
+\newunicodechar{μ}{$\mu$}
+\newunicodechar{κ}{$\kappa$}
+\newunicodechar{π}{$\pi$}
+\newunicodechar{⊞}{$\boxplus$}
+\newunicodechar{⊠}{$\boxtimes$}
+\newunicodechar{∁}{$\mathbb{C}$}
+\newunicodechar{►}{$\blacktriangleright$}
+\newunicodechar{▻}{$\vartriangleright$}
+\newunicodechar{𝟙}{\textbf{1}}
 \newunicodechar{∙}{$\cdot$}
-
+\newunicodechar{∀}{$\forall$}
+\newunicodechar{ℓ}{$\ell$}
+\newunicodechar{∅}{$\varnothing$}
+\newunicodechar{⟶}{$\rightarrow$}
+\newunicodechar{□}{$\square$}
+\newunicodechar{⇡}{$\uparrow$}
+\newunicodechar{⊛}{$\circledast$}
+\newunicodechar{⊎}{$\uplus$}
+\newunicodechar{⟨}{$\langle$}
+\newunicodechar{⟩}{$\rangle$}
+\newunicodechar{∎}{$\blacksquare$}
+\newunicodechar{⇒}{$\Rightarrow$}
+\newunicodechar{⊕}{$\oplus$}
+\newunicodechar{⊗}{$\otimes$}
+\newunicodechar{∼}{$\sim$}
+\newunicodechar{≈}{$\approx$}
+\newunicodechar{⊔}{$\sqcup$}
+\newunicodechar{⟦}{$\llbracket$}
+\newunicodechar{⟧}{$\rrbracket$}
+\newunicodechar{⊥}{$\bot$}
 % Add more as you need them (shouldn't happen often).
@@
 \newcommand{\Fi}{\AgdaField}
+\newcommand{\AgdaUnderscore}{\_}
 
@@
 \section{Preliminaries}
-%% \input{Prelude/Basics}
+\input{Prelude/Basics}
 %% \input{Presheaves/Presheaves}
@@
 
-\subsection{Guarded Recursive Type Theory}
+\section{Deep Embedding}
+\input{Prelude/Syntax}
 
-\section{Presheaves}
-A presheaf is a functor from the category of sizes to \D{Set}.
-
+\section{Presheaf Semantics}
+\subsection{Presheaaves}
 \input{Presheaves/Presheaves}
 
-Every type \Ar{A} in \D{Set} defines a constant presheaf whose action
-on \Ar{i} is given by \Ar{A}, for any size \Ar{i}.
 \input{Presheaves/Const}
 
-Presheaves are the objects of a category whose morphisms are natural
-transformations. This is a cartesian closed category with finite
-coproducts.
-The terminal object is the constant presheaf on the unit type \D{⊤},
-i.e. \D{Terminal} = \D{Const ⊤}. Given two presheaves \Ar{P} and
-\Ar{Q}, we write \D{Prod} \Ar{P} \Ar{Q} for their cartesian
-product. The action of \D{Prod} \Ar{P} \Ar{Q} on a size \Ar{i} is
-defined as follows:
-\remove{
+\input{Presheaves/Terminal}
+
+\input{Presheaves/Sum}
+
 \input{Presheaves/Product}
-%\Fi{PSh.Obj} \Ar{P i ×} \Fi{PSh.Obj} \Ar{Q i}.
-Coproducts are also defined in a similar pointwise way.
 
-Given two presheaves \Ar{P} and
-\Ar{Q}, we write \D{Exp} \Ar{P} \Ar{Q} for their exponential. 
- The action of \D{Exp} \Ar{P} \Ar{Q} on a size \Ar{i} is
-defined as follows:
 \input{Presheaves/Exp}
-}
-\section{The Model}
 
-\subsection{Types, Contexts, Terms}
+\subsection{Kripke Semantics}
 A context in \IC{set} is an element of \D{Set}. A context in \IC{tot}
@@
 the usual variable, weakening and substitutution operations.
+
+\input{CloTT/Structure/ContextOperations}
+\input{CloTT/Structure/Subst}
 %\subsection{Operations on Contexts}
@@
 
-\subsection{Simple Types}
-
+\section{Modelling Guarded Recursion}
 \subsection{Later}
+\input{CloTT/TypeFormers/Later}
+\input{CloTT/TypeFormers/LaterType}
+\input{CloTT/TypeFormers/Fix}
 
 \subsection{Clock Quantification}
-
-\subsection{Fix}
+\input{CloTT/TypeFormers/ClockQuantification}
+\input{CloTT/TypeFormers/ClockQuantificationType}
 
 \subsection{Inductive Types}
+\input{CloTT/TypeFormers/Mu}
 
 \section{The Interpretation}
+\input{GuardedTT}
 

### 2019-01-10 code-oneclock-paper/latex/CloTT/Structure/ClockContexts.tex
Modified gitignore, clockcontexts in paper

\AgdaHide{
\begin{code}%
\>[0]\AgdaKeyword{module}\AgdaSpace{}%
\AgdaModule{CloTT.Structure.ClockContexts}\AgdaSpace{}%
\AgdaKeyword{where}\<%
\end{code}
}

\begin{code}%
\>[0]\AgdaKeyword{data}\AgdaSpace{}%
\AgdaDatatype{tag}\AgdaSpace{}%
\AgdaSymbol{:}\AgdaSpace{}%
\AgdaPrimitiveType{Set}\AgdaSpace{}%
\AgdaKeyword{where}\<%
\\
\>[0][@{}l@{\AgdaIndent{0}}]%
\>[2]\AgdaInductiveConstructor{set}\AgdaSpace{}%
\AgdaSymbol{:}\AgdaSpace{}%
\AgdaDatatype{tag}\<%
\\
%
\>[2]\AgdaInductiveConstructor{tot}\AgdaSpace{}%
\AgdaSymbol{:}\AgdaSpace{}%
\AgdaDatatype{tag}\<%
\end{code}

### 2019-01-10 code-oneclock-paper/latex/CloTT/Structure/ClockContexts.tex
Added label for sections for references
Work on types/context, added unicode symbols forr syntactic sugar of sigma

@@
 }
+
+Our goal is to make an interpretation of the syntax as defined in \Cref{sec:syntax}.
+For this, we first need to interpret clock contexts and for those there are two possibilities.
+It is either empty or we have a single clock.
+In the first case, we use the tag \AIC{set} to indicate we interpret types and contexts as sets.
+In the second case, we use \AIC{tot}, which says we work in some topos of trees.
 

### 2019-01-10 code-oneclock-paper/latex/paper.tex
more preliminaries
Finished subsection on presheaves
Modified gitignore, clockcontexts in paper
Added label for sections for references
Work on types/context, added unicode symbols forr syntactic sugar of sigma
Modified paper.tex (removed some text)

@@
 \newunicodechar{ε}{$\varepsilon$}
+\newunicodechar{θ}{$\theta$}
 \newunicodechar{λ}{$\lambda$}
@@
 \newunicodechar{π}{$\pi$}
+\newunicodechar{∈}{$\in$}
 \newunicodechar{⊞}{$\boxplus$}
@@
 
+\usepackage{cleveref}
+
 \title{Guarded Recursive Type Theory via Sized Types}
@@
 \section{Introduction}
+\label{sec:intro}
 \cite{atkey2013productive}
@@
 \section{Preliminaries}
+\label{sec:prelim}
 \input{Prelude/Basics}
@@
 %% \input{allcode}
-\subsection{Sized Types}
+%\subsection{Sized Types}
 
 \section{Deep Embedding}
+\label{sec:syntax}
 \input{Prelude/Syntax}
@@
 \section{Presheaf Semantics}
-\subsection{Presheaaves}
+\label{sec:presheaf_sem}
+\subsection{Presheaves}
+\label{sec:presheaves}
 \input{Presheaves/Presheaves}
@@
 \subsection{Kripke Semantics}
-A context in \IC{set} is an element of \D{Set}. A context in \IC{tot}
-is a preasheaf in \D{PSh}.
+\label{sec:kripke}
+\input{CloTT/Structure/ClockContexts}
 
@@
 
-Since we are modeling a simply typed calculus, types are interpreted
-in the same ways as contexts.
-
 \input{CloTT/Structure/Types}
-
-In \IC{set}, a term of type \Ar{A} in context \Ar{Γ} is a function
-from \Ar{Γ} to \Ar{A}. In \IC{tot}, a term of type \Ar{A} in context
-\Ar{Γ} is a natural transformation between the presheaves \Ar{Γ} and
-\Ar{A}.
 

### 2019-01-10 code-oneclock-paper/latex/paper.tex
Newest version of LiPiCS

@@
-\documentclass[a4paper,UKenglish,cleveref, autoref,numberwithinsect]{lipics-v2018}
+\documentclass[a4paper,UKenglish,cleveref, autoref,numberwithinsect]{lipics-v2019}
+
+\title{Guarded Recursive Type Theory via Sized Types}
+
+\titlerunning{Guarded Recursive Type Theory via Sized Types}%optional, please use if title is longer than one line
+
+\author{Niccolo Veltri}{Department of Informatics, Dummy College, [optional: Address], Country}{joanrpublic@dummycollege.org}{[orcid]}{[funding]}
+
+\author{Niels van der Weide}{iCIS, Radboud University, The Netherlands}{nweide@cs.ru.nl}{[orcid]}{}
+
+\authorrunning{N. Veltri and N. van der Weide}%TODO mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et al.'
+
+\Copyright{Niccolo Veltri, Niels van der Weide}
+
+\ccsdesc[100]{General and reference~General literature}
+\ccsdesc[100]{General and reference}%TODO mandatory: Please choose ACM 2012 classifications from https://dl.acm.org/ccs/ccs_flat.cfm
+
+\keywords{Dummy keyword}%TODO mandatory; please add comma-separated list of keywords
+
+\category{}%optional, e.g. invited paper
+
+\relatedversion{}%optional, e.g. full version hosted on arXiv, HAL, or other respository/website
+%\relatedversion{A full version of the paper is available at \url{...}.}
+
+\supplement{}%optional, e.g. related research data, source code, ... hosted on a repository like zenodo, figshare, GitHub, ...
+
+%\funding{(Optional) general funding statement \dots}%optional, to capture a funding statement, which applies to all authors.
+Please enter author specific funding statements as fifth argument of the \author macro.
+
+\acknowledgements{Acknowledge Andrea Vezzosi.}%optional
+
+%\nolinenumbers %uncomment to disable line numbering
+
+%\hideLIPIcs  %uncomment to remove references to LIPIcs series (logo, DOI, ...), e.g. when preparing a pre-final version to be uploaded to arXiv or another public repository
+
+%Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\EventEditors{John Q. Open and Joan R. Access}
+\EventNoEds{2}
+\EventLongTitle{42nd Conference on Very Important Topics (CVIT 2016)}
+\EventShortTitle{CVIT 2016}
+\EventAcronym{CVIT}
+\EventYear{2016}
+\EventDate{December 24--27, 2016}
+\EventLocation{Little Whinging, United Kingdom}
+\EventLogo{}
+\SeriesVolume{42}
+\ArticleNo{23}
+
+\usepackage{csquotes}
+\usepackage[all,cmtip]{xy}
+
+%%%%%%%%%%%%%   AMS MATH  %%%%%%%%%%%%%%
+\usepackage{amsmath}
+\usepackage{amsthm}
+\usepackage{amssymb}
+\usepackage{mathtools}
 
@@
 
-\bibliographystyle{plainurl}% the recommnded bibstyle
-
 \usepackage{cleveref}
 
-\title{Guarded Recursive Type Theory via Sized Types}
+\bibliographystyle{plainurl}% the mandatory bibstyle
 

### 2019-01-11 code-oneclock-paper/latex/paper.tex
Update substitutions
Added the necessary pdfs

@@
 \newunicodechar{₂}{$_2$}
+\newunicodechar{₃}{$_3$}
 \newunicodechar{Γ}{$\Gamma$}
@@
 \newunicodechar{α}{$\alpha$}
+\newunicodechar{β}{$\beta$}
 \newunicodechar{γ}{$\gamma$}
@@
 \subsection{Kripke Semantics}
-\label{sec:kripke}
+%\label{sec:kripke}
 \input{CloTT/Structure/ClockContexts}
@@
 
-Two types in \IC{set} are judgementally equal if and only if they are
-isomorphic as elements of \D{Set}. Two types in \IC{tot} are
-judgementally equal if and only if they are isomorphic as elements of
-\D{PSh}.
-
-Two terms in \IC{set} are judgementally equal if and only if they are
-propositionally equal as functions. Two terms in \IC{tot} are
-judgementally equal if and only if they are propositionally equal as
-natural transformations.
+\input{CloTT/Structure/Subst}
 
@@
 
-We write \D{∙} for the empty context and \Ar{Γ} \D{,,} \Ar{A} for the
-extension of the context \Ar{Γ} with the type \Ar{A}. We have
-the usual variable, weakening and substitutution operations.
-
-\input{CloTT/Structure/ContextOperations}
-\input{CloTT/Structure/Subst}
-%\subsection{Operations on Contexts}
-%\subsection{Substitution}
+%\input{CloTT/Structure/ContextOperations} Context operations and simple type forrmers are not interesting. There is not much to tell about them, so a remark suffices.
 

### 2019-01-11 code-oneclock-paper/latex/Introduction.tex
WIP: beginning of introduction

In dependent type theory, one usually works with terminating computations to ensure consistency.
Yet many interesting programs are not terminating and use possibly infinite data types.
To remain consistent, the computations must be productive \cite{Coquand93}.
This means: every finite part of an infinite object must be compute in a finite number of steps.

To allow convenient programming and reasoning with infinite objects, we need to extend our type theory with productivity checks.
In the previous years, various approaches were developed for such extensions.
One is based on sized types \cite{A-sized,AVW-normalization}, where types are assigned a size to indicate the number of unfoldings.
Another is based on guarded recursion \cite{AtkeyM13,BahrGM17}.

The relation between those approaches...

To compare these two approaches, we develop denotational semantics of guarded recursive type theory in a ttype theory with sized types.
More specifically, we define a presheaf model of a simple type theory with guarded recursion \cite{BMSS-synthetic}.
The interpretation of simple types are obtained via standard presheaf semantics.
However, guarded recursion and guarded recursive types are more difficult to obtain.
Since we use sizes rather than natural numbers, we cannot reuse the topos of trees \cite{BMSS-synthetic}.

### 2019-01-11 code-oneclock-paper/latex/paper.tex
First draft of section 4
Added bibliography
WIP: beginning of introduction

@@
 
-\title{Guarded Recursive Type Theory via Sized Types}
+\title{Guarded Recursion in Agda via Sized Types}
 
@@
 \label{sec:intro}
-\cite{atkey2013productive}
+\input{Introduction}
+\nocite{*}
 
@@
 
-%\input{CloTT/Structure/ContextOperations} Context operations and simple type forrmers are not interesting. There is not much to tell about them, so a remark suffices.
+\input{CloTT/Structure/ContextOperations}
+
+Lastly, we use operations on sets and presheaves to define the type operators in simple type theory.
+For sets, we use products, sums, and function types in Agda.
+Products, sums, and exponentials of presheaves are interpreted with the operations in \Cref{sec:presheaves}.
 

### 2019-01-12 code-oneclock-paper/latex/paper.tex
Some work on Later, fixed bibliography
Macors for ie and so on
Changed order in section 5
Work on µ
Renewed the tex files
author name

@@
 
-\author{Niccolo Veltri}{Department of Informatics, Dummy College, [optional: Address], Country}{joanrpublic@dummycollege.org}{[orcid]}{[funding]}
+\author{Niccol\`o Veltri}{Department of Computer Science, IT
+  University of Copenhagen, Denmark}{nive@itu.dk}{[orcid]}{[funding]}
 
@@
 
-\Copyright{Niccolo Veltri, Niels van der Weide}
+\Copyright{Niccol\`o Veltri, Niels van der Weide}
 
@@
 \newunicodechar{⊥}{$\bot$}
+\newunicodechar{∞}{$\infty$}
 % Add more as you need them (shouldn't happen often).
@@
 
+\newcommand{\ie}{\emph{i.e.,} }
+\newcommand{\cf}{\emph{c.f.} }
+\newcommand{\eg}{\emph{e.g.,} }
+\newcommand{\etal}{\emph{et~al.}}
+\newcommand{\etc}{\emph{etc.}}
+\newcommand{\wrt}{w.r.t.~}
+\newcommand{\resp}{resp.~}
+\newcommand{\loccit}{\emph{loc. cit.} }
+
 %This is a template for producing LIPIcs articles. 
@@
 \bibliographystyle{plainurl}% the mandatory bibstyle
+
+\newcommand{\NV}[1]{\textcolor{green}{NV: #1}}
+\newcommand{\NW}[1]{\textcolor{orange}{NW: #1}}
 
@@
 \section{Modelling Guarded Recursion}
+We model something like guarrded ercursion.
+Oh, and guarded recursive types
+
+\subsection{Clock Quantification}
+\input{CloTT/TypeFormers/WeakenClock}
+\input{CloTT/TypeFormers/ClockQuantification}
+
 \subsection{Later}
 \input{CloTT/TypeFormers/Later}
-\input{CloTT/TypeFormers/LaterType}
 \input{CloTT/TypeFormers/Fix}
-
-\subsection{Clock Quantification}
-\input{CloTT/TypeFormers/ClockQuantification}
-\input{CloTT/TypeFormers/ClockQuantificationType}
+\input{CloTT/TypeFormers/Force}
 

### 2019-01-12 code-oneclock-paper/latex/paper.tex
Fixes

@@
 
-\author{Niccol\`o Veltri}{Department of Computer Science, IT
-  University of Copenhagen, Denmark}{nive@itu.dk}{[orcid]}{[funding]}
+\author{Niccolo Veltri}{Department of Informatics, Dummy College, [optional: Address], Country}{joanrpublic@dummycollege.org}{[orcid]}{[funding]}
 
@@
 
-\Copyright{Niccol\`o Veltri, Niels van der Weide}
+\Copyright{Niccolo Veltri, Niels van der Weide}
 
@@
 \newunicodechar{⟩}{$\rangle$}
+\newunicodechar{■}{$\blacksquare$}
 \newunicodechar{∎}{$\blacksquare$}
@@
 
+\input{Presheaves/NaturalTransformations}
+
 \input{Presheaves/Const}
@@
 %\label{sec:kripke}
-\input{CloTT/Structure/ClockContexts}
-
 \input{CloTT/Structure/Contexts}

### 2019-01-12 code-oneclock-paper/latex/paper.tex
new symbol for weakenC and weakenT in syntax
Minor additions to text, removed appendix.

--- 2019-01-12 code-oneclock-paper/latex/paper.tex
@@
 \newunicodechar{∞}{$\infty$}
+\newunicodechar{⇑}{$\Uparrow$}
 % Add more as you need them (shouldn't happen often).
@@
 Products, sums, and exponentials of presheaves are interpreted with the operations in \Cref{sec:presheaves}.
+We only give the notation for function types.
+
+\input{CloTT/TypeFormers/FunctionType}
 
 \section{Modelling Guarded Recursion}
-We model something like guarrded ercursion.
-Oh, and guarded recursive types
+Now we got the simple type formers and their terms.
+The next step is add the type formers required for guarded recursion.
+We start by defining clock quantification and later, and how to construct terms of those types.
+In addition, we define the fixpoint combinator.
+We end this section by giving a type former for guarded recursive types.
 
@@
 
-\appendix
-\section{Omitted Proofs}
-
 %%

### 2019-01-13 code-oneclock-paper/latex/Introduction.tex
Some work on Later, fixed bibliography
Small fixes
Furter work on introduction

@@
 To remain consistent, the computations must be productive \cite{Coquand93}.
-This means: every finite part of an infinite object must be compute in a finite number of steps.
+This means: every finite part of an infinite object can be computed in a finite number of steps.
 
 To allow convenient programming and reasoning with infinite objects, we need to extend our type theory with productivity checks.
-In the previous years, various approaches were developed for such extensions.
+To this end, various approaches have been developed.
 One is based on sized types \cite{A-sized,AVW-normalization}, where types are assigned a size to indicate the number of unfoldings.
-Another is based on guarded recursion \cite{AtkeyM13,BahrGM17}.
+These are implemented in Agda \cite{norell2008}.
+Another is based on guarded recursion \cite{atkey2013productive,BahrGM17}, where the type theory is extended with a general fixpoint combinator.
+At the current moment, there is no proof assistant based on guarded recursion.
 
@@
 
-To compare these two approaches, we develop denotational semantics of guarded recursive type theory in a ttype theory with sized types.
+To compare these two approaches, we develop denotational semantics of guarded recursive type theory in a type theory with sized types.
 More specifically, we define a presheaf model of a simple type theory with guarded recursion \cite{BMSS-synthetic}.
-The interpretation of simple types are obtained via standard presheaf semantics.
-However, guarded recursion and guarded recursive types are more difficult to obtain.
-Since we use sizes rather than natural numbers, we cannot reuse the topos of trees \cite{BMSS-synthetic}.
+Simple types are interpreted via the usual presheaf semantics.
+
+However, the challenge lies in interpreting guarded recursion and guarded recursive types.
+The most common model in the literature is the topos of trees \cite{BMSS-synthetic}.
+This is a presheaf topos, whose objects are sets indexed by a natural number.
+We use a slightly different approach: instead of natural numbers, we use sizes.
+This means that the required interpretations need to be modified.
+
+Our contributions are as follows
+\begin{enumerate}
+	\item We give a new model of guarded recursive type theory;
+	\item We give a formal relation between sized types and guarded recursion;
+	\item The construction is formalized.
+\end{enumerate}
+
+In Section 2, we describe the meta-theory in which we work.
+In Section 3, we describe the object theory.
+This is basically a variant of guarded recursion as done by Atkey and McBride \cite{atkey2013productive}.
+In Section 4, we define the model and give the interpretation of simple type operators.
+In Section 5, we interpret guarded recursion and guarded recursive types.
+Finally, we give an overview of the interpretation in Section 6.
+
+\NW{Perhaps related work needs to be a separate section before conclusion. Alternatively, we can put it before the contributions (I think this is better)}
+
+\subsection*{Related Work}

### 2019-01-13 code-oneclock-paper/latex/paper.tex
Fixed running title
More elegant solution to make LiPiCS work with agda.sty
Added orcid

@@
 
-\titlerunning{Guarded Recursive Type Theory via Sized Types}%optional, please use if title is longer than one line
-
 \author{Niccol\`o Veltri}{Department of Computer Science, IT
@@
 
-\author{Niels van der Weide}{iCIS, Radboud University, The Netherlands}{nweide@cs.ru.nl}{[orcid]}{}
+\author{Niels van der Weide}{iCIS, Radboud University, The Netherlands}{nweide@cs.ru.nl}{https://orcid.org/0000-0003-1146-4161}{}
 
@@
 
-\usepackage{agda}
+\usepackage[noinputencodingsetup]{agda}
 
@@
 \newcommand{\Fi}{\AgdaField}
-\newcommand{\AgdaUnderscore}{\_}
 

### 2019-01-14 code-oneclock-paper/latex/paper.tex
WIP deep embedding
worked on dfix and force
Added example of streams to tex file
rephrasing deep emb
more work on deep emb
Added keywords and classification

@@
 
-\ccsdesc[100]{General and reference~General literature}
-\ccsdesc[100]{General and reference}%TODO mandatory: Please choose ACM 2012 classifications from https://dl.acm.org/ccs/ccs_flat.cfm
+\ccsdesc[100]{Theory of Computation~Type Theory}
+\ccsdesc[100]{Theory of Computation~Categorical Semantics}%TODO mandatory: Please choose ACM 2012 classifications from https://dl.acm.org/ccs/ccs_flat.cfm
 
-\keywords{Dummy keyword}%TODO mandatory; please add comma-separated list of keywords
+\keywords{guarded recursion, type theory, semantics, coinduction, sized types}%TODO mandatory; please add comma-separated list of keywords
 
@@
 \newunicodechar{β}{$\beta$}
+\newunicodechar{η}{$\eta$}
 \newunicodechar{γ}{$\gamma$}
@@
 \newcommand{\loccit}{\emph{loc. cit.} }
+
+\newcommand{\GTT}{\textbf{GTT}}
 
@@
 \input{Prelude/Syntax}
+\input{Streams}
 
@@
 
-\subsection{Clock Quantification}
+\subsection{Context Weakening and Clock Quantification}
 \input{CloTT/TypeFormers/WeakenClock}
@@
 
-\subsection{Later}
+\subsection{The Later Modality}
 \input{CloTT/TypeFormers/Later}

### 2019-01-14 code-oneclock-paper/latex/paper.tex
Fixedd affiliation

@@
 
-\author{Niels van der Weide}{iCIS, Radboud University, The Netherlands}{nweide@cs.ru.nl}{https://orcid.org/0000-0003-1146-4161}{}
+\author{Niels van der Weide}{Institute for Computation and Information Sciences, Radboud University, The Netherlands}{nweide@cs.ru.nl}{https://orcid.org/0000-0003-1146-4161}{}
 

### 2019-01-14 code-oneclock-paper/latex/paper.tex
First version of section 6 (The Interpretation)
Some textual fixes in sections 2 and 3

@@
 \section{Presheaf Semantics}
+Next we define categorical semantics for the syntax defined in \Cref{sec:syntax}.
+To do so, we use a similar method as used by M{\o}gelberg \cite{Mogelberg14}.
+The interpretation of types depend on the clock contexts.
+If the clock context is empty, then types become sets.
+If the clock context has one clock, then types are interpreted as objects in the topos of trees.
+
 \label{sec:presheaf_sem}
@@
 \input{Presheaves/Const}
-
-\input{Presheaves/Terminal}
-
-\input{Presheaves/Sum}
-
-\input{Presheaves/Product}
-
-\input{Presheaves/Exp}
 
@@
 \section{Modelling Guarded Recursion}
+\label{sec:guarded}
 Now we got the simple type formers and their terms.

### 2019-01-15 code-oneclock-paper/latex/Introduction.tex
Minor fixes in the text

@@
 
-However, the challenge lies in interpreting guarded recursion and guarded recursive types.
+In contrast, interpreting guarded recursion and guarded recursive types is more challenging.
 The most common model in the literature is the topos of trees \cite{BMSS-synthetic}.
@@
 
-\NW{Perhaps related work needs to be a separate section before conclusion. Alternatively, we can put it before the contributions (I think this is better)}
-
 \subsection*{Related Work}

### 2019-01-15 code-oneclock-paper/latex/paper.tex
Rewrite in the text of fix
Minor fixes in the text

@@
 
+\input{Presheaves/Exp}
+
 \subsection{Kripke Semantics}
@@
 \label{sec:guarded}
-Now we got the simple type formers and their terms.
-The next step is add the type formers required for guarded recursion.
-We start by defining clock quantification and later, and how to construct terms of those types.
+Now we have the simple type formers and their terms.
+The next step is to add the type formers required for guarded recursion.
+We start by defining clock quantification and the later modality, and how to construct terms of those types.
 In addition, we define the fixpoint combinator.

### 2019-01-15 code-oneclock-paper/latex/paper.tex
rephrased sizes
Reamed some titles
Added a conclusion

@@
 
-\section{Presheaf Semantics}
+\section{Categorical Semantics}
 Next we define categorical semantics for the syntax defined in \Cref{sec:syntax}.
@@
 
-\subsection{Kripke Semantics}
+\subsection{Simple Type Theory in Presheaves}
 %\label{sec:kripke}
@@
 
-\subsection{Inductive Types}
+\subsection{Guarded Recursive Types}
 \input{CloTT/TypeFormers/Mu}
 
-\section{The Interpretation}
+\section{Consistency}
 \input{GuardedTT}
@@
 \section{Conclusion}
+We formally defined a syntax of guarded type theory with explicit substitutions and weakening, and we constructed denotational semantics for it in type theory extended with sized types.
+From this, we concluded that this theory is consistent and that guarded recursion can be defined via sized types.
+
+There are several possible ways to improve on this result.
+First of all, one could define a dependent version of this type theory extended with multiple clocks.
+This can be done in two ways.
+Either one extends the object theory with delayed substitutions \cite{bizjak2016guarded} or with ticks \cite{BahrGM17}.
+Second of all, with the deep embedding in place, one can further study the meta-theory by defining a formalized type checking and a normalization algorithm.
 

### 2019-01-15 code-oneclock-paper/latex/Introduction.tex
Work on introduction

@@
 
-The relation between those approaches...
-
-To compare these two approaches, we develop denotational semantics of guarded recursive type theory in a type theory with sized types.
+To compare the strength of these two approaches, we develop denotational semantics of guarded recursive type theory in a type theory with sized types.
+This shows that guarded recursive type theory can be done via sized types.
 More specifically, we define a presheaf model of a simple type theory with guarded recursion \cite{BMSS-synthetic}.
@@
 \begin{enumerate}
-	\item We give a new model of guarded recursive type theory;
-	\item We give a formal relation between sized types and guarded recursion;
-	\item The construction is formalized.
+	\item We give a new denotational semantics of guarded recursive type theory in type theory;
+	\item We show that guarded recursion can be interpreted in sized types.
+	\item We formally prove the syntax is consistent.
 \end{enumerate}
@@
 In Section 2, we describe the meta-theory in which we work.
-In Section 3, we describe the object theory.
-This is basically a variant of guarded recursion as done by Atkey and McBride \cite{atkey2013productive}.
-In Section 4, we define the model and give the interpretation of simple type operators.
-In Section 5, we interpret guarded recursion and guarded recursive types.
-Finally, we give an overview of the interpretation in Section 6.
+In Section 3, we describe the syntax of the object theory, which is basically a variant of guarded recursion as done by Atkey and McBride \cite{atkey2013productive}.
+We do this in the form of a deep embedding.
+More specifically, we define data types representing the contexts, types, terms, and so on, and we give the rules for definitional equality.
+In Sections 4 and 5, we define the denotational semantics of this syntax.
+First, we give the interpretation of context, types, and terms in the model, and we show how to interpret simple type formers.
+Then we show this model supports guarded recursion and guarded recursive types.
+Finally, we show the syntax is consistent in Section 6.
 

### 2019-01-15 code-oneclock-paper/latex/paper.tex
acks, funding, orcid

@@
 \author{Niccol\`o Veltri}{Department of Computer Science, IT
-  University of Copenhagen, Denmark}{nive@itu.dk}{[orcid]}{[funding]}
+  University of Copenhagen, Denmark}{nive@itu.dk}{https://orcid.org/0000-0002-7230-3436}{This work was supported by a research grant (13156) from VILLUM FONDEN,
+  and by DFF-Research Project 1 Grant no. 4002-00442, from The Danish Council 
+  for Independent Research for the Natural Sciences (FNU).}
 
@@
 
-\acknowledgements{Acknowledge Andrea Vezzosi.}%optional
+\acknowledgements{We are thankful to Andreas Abel, Herman Geuvers,
+  Rasmus Ejlers M{\o}gelberg and Andrea Vezzosi for discussions and
+valuable hints.}%optional
 
@@
 \subsection{The Later Modality}
+\label{sec:later}
 \input{CloTT/TypeFormers/Later}

### 2019-01-16 code-oneclock-paper/latex/paper.tex
Fixed affiliation

@@
 
-\author{Niels van der Weide}{Institute for Computation and Information Sciences, Radboud University, The Netherlands}{nweide@cs.ru.nl}{https://orcid.org/0000-0003-1146-4161}{}
+\author{Niels van der Weide}{Institute for Computation and Information Sciences, Radboud University, Nijmegen, The Netherlands}{nweide@cs.ru.nl}{https://orcid.org/0000-0003-1146-4161}{}
 

### 2019-01-17 code-oneclock-paper/latex/Introduction.tex
rephrasing intro

@@
-In dependent type theory, one usually works with terminating computations to ensure consistency.
-Yet many interesting programs are not terminating and use possibly infinite data types.
-To remain consistent, the computations must be productive \cite{Coquand93}.
-This means: every finite part of an infinite object can be computed in a finite number of steps.
+Dependent type theory is a very expressive functional programming
+language that underlies the deductive system of proof assistants such
+as Coq, Agda \cite{norell2008} and Lean.  It is a total language,
+meaning that every program definable inside type theory is necessarily
+terminating. This is an important requirement that ensures the
+consistency of the type system.
 
-To allow convenient programming and reasoning with infinite objects, we need to extend our type theory with productivity checks.
-To this end, various approaches have been developed.
-One is based on sized types \cite{A-sized,AVW-normalization}, where types are assigned a size to indicate the number of unfoldings.
-These are implemented in Agda \cite{norell2008}.
-Another is based on guarded recursion \cite{atkey2013productive,BahrGM17}, where the type theory is extended with a general fixpoint combinator.
-At the current moment, there is no proof assistant based on guarded recursion.
+Possibly non-terminating computations
+and infinite structures such as non-wellfounded trees can be
+represented in type theory by extending the type system with
+coinductive types. Elements of these types, which we call processes,
+are required to be productive \cite{Coquand93} in the sense that every
+finite unfolding can be computed in a finite number of steps.
+In Agda's encoding of coinductive types using ``musical notation''
+\NV{Citation? What about Coq?}, productivity is achieved using a strict method: in the
+definition of corecursive functions, the recursive
+call is required to appear directly under
+the application of a constructor. This restriction
+typically makes programming with processes cumbersome,
+which spawned the search for alternative techniques for ensuring the
+well-definedness of corecursive definitions.
+
+We focus on two of these techniques in which productivity is encoded
+at the level of types: sized types and guarded recursion. A sized type
+\NV{Cite Huges?} is a type annotated with the number of unfolding that
+elements of this type can undergo. Sized types have been implemented
+in Agda \cite{A-sized,AVW-normalization} and can be used in
+combination with coinductive records \NV{Cite Copatterns?} for the
+specification of coinductive types.  Guarded recursion \NV{Cite
+  Nakano?} is a different approach where the type system is enhanced
+with a modality, called ``later'' and written \IC{▻}, encoding time
+delay in types. The later modality comes with a general fixpoint
+combinator for programming with productive recursive functions and
+allows the specification of guarded recursive types, \eg the
+type of guarded streams satisfying the isomorphism \F{Str}
+\Ar{A} \F{≃} \Ar{A} \F{×} \IC{▻} (\F{Str} \F{A}). The tail
+of a guarded stream is available only one time step ahead from now, as
+evidenced by the application of the later modality to \F{Str}
+\F{A}. Coinductive types can be constructed from guarded recursive
+types in type theories that additionally support clock variables and
+universal quantification over them
+\cite{atkey2013productive,BahrGM17}. An implementation of
+calculi with guarded recursion is currently missing.
+%%  nor guarded recursion
+%% appears as a selectable feature in a proof assistant.
+
+%% In recent years we witnessed
+%% the development of several type theories with primitive support for guarded
+%% recursion \cite{atkey2013productive,BahrGM17}.
+
+%% In dependent type theory, one usually works with terminating
+%% computations to ensure consistency.  Yet many interesting programs are
+%% not terminating and use possibly infinite data types.  To remain
+%% consistent, the computations must be productive.  This means: every
+%% finite part of an infinite object can be computed in a finite number
+%% of steps.
+
+%% To allow convenient programming and reasoning with infinite objects, we need to extend our type theory with productivity checks.
+%% To this end, various approaches have been developed.
+%% One is based on sized types \cite{A-sized,AVW-normalization}, where types are assigned a size to indicate the number of unfoldings.
+%% These are implemented in Agda \cite{norell2008}.
+%% Another is based on guarded recursion \cite{atkey2013productive,BahrGM17}, where the type theory is extended with a general fixpoint combinator.
+%% At the current moment, there is no proof assistant based on guarded recursion.
+
+\NV{WIP from this point}
 
@@
 
-\subsection*{Related Work}
+%% \subsection{Related Work}
+%% 
+%% Guarded recursion via the later modality was introduced by Nakano \NV{Citation}.

### 2019-01-17 code-oneclock-paper/latex/Introduction.tex
WIP intro

@@
 language that underlies the deductive system of proof assistants such
-as Coq, Agda \cite{norell2008} and Lean.  It is a total language,
+as Coq, Agda and Lean.  It is a total language,
 meaning that every program definable inside type theory is necessarily
@@
 In Agda's encoding of coinductive types using ``musical notation''
-\NV{Citation? What about Coq?}, productivity is achieved using a strict method: in the
+\cite{DA10} \NV{What about Coq?}, productivity is achieved using a strict method: in the
 definition of corecursive functions, the recursive
@@
 at the level of types: sized types and guarded recursion. A sized type
-\NV{Cite Huges?} is a type annotated with the number of unfolding that
+\cite{Hughes96} is a type annotated with the number of unfolding that
 elements of this type can undergo. Sized types have been implemented
 in Agda \cite{A-sized,AVW-normalization} and can be used in
-combination with coinductive records \NV{Cite Copatterns?} for the
-specification of coinductive types.  Guarded recursion \NV{Cite
-  Nakano?} is a different approach where the type system is enhanced
-with a modality, called ``later'' and written \IC{▻}, encoding time
-delay in types. The later modality comes with a general fixpoint
-combinator for programming with productive recursive functions and
-allows the specification of guarded recursive types, \eg the
-type of guarded streams satisfying the isomorphism \F{Str}
-\Ar{A} \F{≃} \Ar{A} \F{×} \IC{▻} (\F{Str} \F{A}). The tail
-of a guarded stream is available only one time step ahead from now, as
-evidenced by the application of the later modality to \F{Str}
-\F{A}. Coinductive types can be constructed from guarded recursive
-types in type theories that additionally support clock variables and
-universal quantification over them
-\cite{atkey2013productive,BahrGM17}. An implementation of
-calculi with guarded recursion is currently missing.
+combination with coinductive records for the specification of
+coinductive types \cite{Copatterns}.  Guarded recursion \cite{Nakano}
+is a different approach where the type system is enhanced with a
+modality, called ``later'' and written \IC{▻}, encoding time delay in
+types. The later modality comes with a general fixpoint combinator for
+programming with productive recursive functions and allows the
+specification of guarded recursive types, \eg the type of guarded
+streams satisfying the isomorphism \F{Str} \Ar{A} \F{≃} \Ar{A} \F{×}
+\IC{▻} (\F{Str} \F{A}). The tail of a guarded stream is available only
+one time step ahead from now, as evidenced by the application of the
+later modality to \F{Str} \F{A}. Coinductive types can be constructed
+from guarded recursive types in type theories that additionally
+support clock variables and universal quantification over them
+\cite{atkey2013productive,BahrGM17}. Currently there is no
+implementation of a calculus with guarded recursion.
 %%  nor guarded recursion
@@
 %% At the current moment, there is no proof assistant based on guarded recursion.
+
+Sized types and guarded recursion are different solution to the same
+problem, but a thorough study of the relation between these two
+disciplines is still missing. In this paper we take a first step in
+this direction by showing how guarded recursion can be simulated in
+Agda using sized types.
 

### 2019-01-17 code-oneclock-paper/latex/Introduction.tex
WIP: intro

@@
 
+Using techniques for representing ``type theory in type theory''
+\cite{Chapman09,AltenkirchK16}, in Section \ref{sec:syntax} we present
+an Agda formalization of the syntax of a simple type theory with
+guarded recursion. This object language, that we call \GTT, is a variant of Atkey and
+McBride's type system for productive coprogramming
+\cite{atkey2013productive} in which the clock context can contain at
+most one clock.
+
+In Section \ref{sec:presheaf_sem}, we develop a denotational semantics
+for \GTT\ using sized types. More precisely, we define a presheaf
+model where the type formers of simply typed lambda calculus are
+evaluated using the standard Kripke semantics. Typically the semantics
+of type theories for guarded recursion is given in the topos of
+trees or variations thereof \cite{BMSS-synthetic} \NV{Add citations here}.
+In order to make clear the connections between guarded recursion and
+sized types, we take the preorder of sizes as the indexing
+category of our presheaves. This means that types and contexts of \GTT\ are
+interpreted as antitone sized types.
+
 \NV{WIP from this point}
 
-To compare the strength of these two approaches, we develop denotational semantics of guarded recursive type theory in a type theory with sized types.
-This shows that guarded recursive type theory can be done via sized types.
-More specifically, we define a presheaf model of a simple type theory with guarded recursion \cite{BMSS-synthetic}.
-Simple types are interpreted via the usual presheaf semantics.
+%% To compare the strength of these two approaches, we develop denotational semantics of guarded recursive type theory in a type theory with sized types.
+%% This shows that guarded recursive type theory can be done via sized types.
+%% More specifically, we define a presheaf model of a simple type theory with guarded recursion \cite{BMSS-synthetic}.
+%% Simple types are interpreted via the usual presheaf semantics.
 

### 2019-01-24 code-oneclock-paper/latex/Introduction.tex
finished intro

@@
 represented in type theory by extending the type system with
-coinductive types. Elements of these types, which we call processes,
+coinductive types. Recursively defined elements of these types
 are required to be productive \cite{Coquand93} in the sense that every
@@
 In Agda's encoding of coinductive types using ``musical notation''
-\cite{DA10} \NV{What about Coq?}, productivity is achieved using a strict method: in the
-definition of corecursive functions, the recursive
+\cite{DA10}, productivity is enforced via a strict obligation: in the
+definition of a corecursive function, the recursive
 call is required to appear directly under
-the application of a constructor. This restriction
-typically makes programming with processes cumbersome,
+the application of a constructor. A similar syntactic
+check is employed in Coq.
+This restriction
+typically makes programming with coinductive types cumbersome,
 which spawned the search for alternative techniques for ensuring the
@@
 
-Using techniques for representing ``type theory in type theory''
-\cite{Chapman09,AltenkirchK16}, in Section \ref{sec:syntax} we present
+Utilizing techniques for representing ``type theory in type theory''
+\cite{Chapman09,AltenkirchK16}, we present
 an Agda formalization of the syntax of a simple type theory with
@@
 \cite{atkey2013productive} in which the clock context can contain at
-most one clock.
+most one clock. The types of \GTT\ include the aformentioned \IC{▻} modality and a
+\IC{□}  modality, the nameless analogue of  Atkey and
+McBride's universal clock quantification.
 
-In Section \ref{sec:presheaf_sem}, we develop a denotational semantics
+Afterwards we develop a categorical semantics
 for \GTT\ using sized types. More precisely, we define a presheaf
@@
 of type theories for guarded recursion is given in the topos of
-trees or variations thereof \cite{BMSS-synthetic} \NV{Add citations here}.
-In order to make clear the connections between guarded recursion and
+trees or variations thereof \cite{BMSS-synthetic,Mogelberg14,MannaaM18}.
+Here, in order to make clear the connections between guarded recursion and
 sized types, we take the preorder of sizes as the indexing
@@
 interpreted as antitone sized types. 
+The well-order relation on sizes is fundamental for giving a
+terminating definition of the semantic fixpoint combinator.
 
-\NV{WIP from this point}
+%% A detailed account of how to model the characteristic features of
+%% \GTT, consisting of the \IC{▻} and
+%% \IC{□}  modality together with guarded recursive types, is given in
+%% Section \ref{sec:guarded}.
+
+To summarize, the contributions of this paper are twofold:
+\begin{enumerate}
+  \item We formalize syntax and semantics of a type theory with
+    guarded recursion in Agda. This is the first such denotational model developed using an extension of Martin-L\"of intensional
+    type theory as the metalanguage, in contrast with the previous
+    set-theoretic models of guarded recursion.
+\item The interpretation of the characteristic features of guarded
+  recursion crucially requires the employment of sized types. This shows that
+  guarded recursive types can be reduced to sized types and
+  constitutes a stepping stone towards a clear understanding of  the connections
+  between different approaches to productive coprogramming.
+%	\item We formally prove the syntax is consistent.
+\end{enumerate}
+
+This paper only include the essential parts of our Agda
+formalization. The full code is available at
+\url{https://github.com/niccoloveltri/agda-clott}. The formalization
+uses Agda 2.5.4.1 and Agda standard library 0.16.
+
+%\NV{WIP from this point}
 
@@
 
-In contrast, interpreting guarded recursion and guarded recursive types is more challenging.
-The most common model in the literature is the topos of trees \cite{BMSS-synthetic}.
-This is a presheaf topos, whose objects are sets indexed by a natural number.
-We use a slightly different approach: instead of natural numbers, we use sizes.
-This means that the required interpretations need to be modified.
+%% In contrast, interpreting guarded recursion and guarded recursive types is more challenging.
+%% The most common model in the literature is the topos of trees \cite{BMSS-synthetic}.
+%% This is a presheaf topos, whose objects are sets indexed by a natural number.
+%% We use a slightly different approach: instead of natural numbers, we use sizes.
+%% This means that the required interpretations need to be modified.
 
-Our contributions are as follows
-\begin{enumerate}
-	\item We give a new denotational semantics of guarded recursive type theory in type theory;
-	\item We show that guarded recursion can be interpreted in sized types.
-	\item We formally prove the syntax is consistent.
-\end{enumerate}
+%% Our contributions are as follows
 
-In Section 2, we describe the meta-theory in which we work.
-In Section 3, we describe the syntax of the object theory, which is basically a variant of guarded recursion as done by Atkey and McBride \cite{atkey2013productive}.
-We do this in the form of a deep embedding.
-More specifically, we define data types representing the contexts, types, terms, and so on, and we give the rules for definitional equality.
-In Sections 4 and 5, we define the denotational semantics of this syntax.
-First, we give the interpretation of context, types, and terms in the model, and we show how to interpret simple type formers.
-Then we show this model supports guarded recursion and guarded recursive types.
-Finally, we show the syntax is consistent in Section 6.
+%% In Section 2, we describe the meta-theory in which we work.
+%% In Section 3, we describe the syntax of the object theory, which is basically a variant of guarded recursion as done by Atkey and McBride \cite{atkey2013productive}.
+%% We do this in the form of a deep embedding.
+%% More specifically, we define data types representing the contexts, types, terms, and so on, and we give the rules for definitional equality.
+%% In Sections 4 and 5, we define the denotational semantics of this syntax.
+%% First, we give the interpretation of context, types, and terms in the model, and we show how to interpret simple type formers.
+%% Then we show this model supports guarded recursion and guarded recursive types.
+%% Finally, we show the syntax is consistent in Section 6.
 

### 2019-01-24 code-oneclock-paper/latex/paper.tex
rephrasing intro
WIP: intro
finished intro

@@
 
-\acknowledgements{We are thankful to Andreas Abel, Herman Geuvers,
+\acknowledgements{We are thankful to Andreas Abel, Guillaume Allais, Herman Geuvers,
   Rasmus Ejlers M{\o}gelberg and Andrea Vezzosi for discussions and
@@
 \newunicodechar{⇑}{$\Uparrow$}
+\newunicodechar{≃}{$\simeq$}
 % Add more as you need them (shouldn't happen often).
@@
 \input{Introduction}
-\nocite{*}
+%\nocite{*}
 
@@
 
-\section{Deep Embedding}
+\section{The Object Type Theory}
 \label{sec:syntax}
@@
 \section{Categorical Semantics}
+
 Next we define categorical semantics for the syntax defined in \Cref{sec:syntax}.
@@
 
-\subsection{Simple Type Theory in Presheaves}
+\subsection{Modelling Simple Type Theory}
 %\label{sec:kripke}

### 2019-01-25 code-oneclock-paper/latex/Introduction.tex
added a couple of comments
comments on Clouston et al. and Abel & Vezzosi in intro

@@
 Utilizing techniques for representing ``type theory in type theory''
-\cite{Chapman09,AltenkirchK16}, we present
-an Agda formalization of the syntax of a simple type theory with
-guarded recursion. This object language, that we call \GTT, is a variant of Atkey and
-McBride's type system for productive coprogramming
-\cite{atkey2013productive} in which the clock context can contain at
-most one clock. The types of \GTT\ include the aformentioned \IC{▻} modality and a
-\IC{□}  modality, the nameless analogue of  Atkey and
-McBride's universal clock quantification.
+\cite{Chapman09,AltenkirchK16}, we present an Agda formalization of
+the syntax of a simple type theory with guarded recursion. This object
+language, that we call \GTT, is a variant of Atkey and McBride's type
+system for productive coprogramming \cite{atkey2013productive} in
+which the clock context can contain at most one clock. The types of
+\GTT\ include the aformentioned \IC{▻} modality and a \IC{□} modality,
+a nameless analogue of Atkey and McBride's universal clock
+quantification. Clouston et al. \cite{CloustonBGB15} have studied a
+guarded variant of lambda calculus extended with a \IC{□} operation,
+which they call ``constant'' .  Our object calculus differs from
+theirs in that our judgments are indexed by a clock context, which can
+be empty or containing exactly one clock. In this respect \GTT\ is
+closer in spirit to Atkey and McBride's language. The design of \GTT\
+also has the benefit of allowing a more pleasant introduction rule for
+\IC{□} than Clouston et al.'s.
 
@@
 interpreted as antitone sized types. 
-The well-order relation on sizes is fundamental for giving a
+The well-order relation on sizes is fundamental for constructing a
 terminating definition of the semantic fixpoint combinator.
+
+Abel and Vezzosi \cite{AbelV14} have also formalized a simple type theory
+extended with the later modality in Agda. They focus on operational
+properties of the calculus and give a certified proof of strong
+normalization. In our work we consider a richer type system and we
+formalize its denotational semantics in Agda. Nevertheless, we do not
+investigate the dynamic behaviour of our calculus, which we leave to
+future work.
 
@@
 \url{https://github.com/niccoloveltri/agda-clott}. The formalization
-uses Agda 2.5.4.1 and Agda standard library 0.16.
+uses Agda 2.5.4.1 and Agda standard library 0.16. The paper is
+extracted from a literate Agda file, which implies that all the
+displayed code has passed Agda's type-check.
 

### 2019-01-26 code-oneclock-paper/latex/Introduction.tex
Fixes in introduction

@@
-Dependent type theory is a very expressive functional programming
+Dependent type theory is an expressive functional programming
 language that underlies the deductive system of proof assistants such
@@
 in Agda \cite{A-sized,AVW-normalization} and can be used in
-combination with coinductive records for the specification of
+combination with coinductive records to specify
 coinductive types \cite{Copatterns}.  Guarded recursion \cite{Nakano}
@@
 
-Sized types and guarded recursion are different solution to the same
+Sized types and guarded recursion are different solutions to the same
 problem, but a thorough study of the relation between these two
@@
 Utilizing techniques for representing ``type theory in type theory''
-\cite{Chapman09,AltenkirchK16}, we present an Agda formalization of
+\cite{AltenkirchK16,Chapman09}, we present an Agda formalization of
 the syntax of a simple type theory with guarded recursion. This object
-language, that we call \GTT, is a variant of Atkey and McBride's type
+language, which we call \GTT, is a variant of Atkey and McBride's type
 system for productive coprogramming \cite{atkey2013productive} in
@@
 a nameless analogue of Atkey and McBride's universal clock
-quantification. Clouston et al. \cite{CloustonBGB15} have studied a
+quantification. Clouston \etal \cite{CloustonBGB15} studied a
 guarded variant of lambda calculus extended with a \IC{□} operation,
@@
 closer in spirit to Atkey and McBride's language. The design of \GTT\
-also has the benefit of allowing a more pleasant introduction rule for
+also has the benefit of allowing a more appealing introduction rule for
 \IC{□} than Clouston et al.'s.
@@
 of type theories for guarded recursion is given in the topos of
-trees or variations thereof \cite{BMSS-synthetic,Mogelberg14,MannaaM18}.
-Here, in order to make clear the connections between guarded recursion and
+trees or variations thereof \cite{BMSS-synthetic,MannaaM18,Mogelberg14}.
+Here, to clarify the connection between guarded recursion and
 sized types, we take the preorder of sizes as the indexing
@@
 
-Abel and Vezzosi \cite{AbelV14} have also formalized a simple type theory
+Abel and Vezzosi \cite{AbelV14} also formalized a simple type theory
 extended with the later modality in Agda. They focus on operational

### 2019-01-27 code-oneclock-paper/latex/paper.tex
constructor down in Subst and associated equalities
Rewriting
Shortening in definition of const
First version of an abstract

@@
 \newunicodechar{≃}{$\simeq$}
+\newunicodechar{∘}{$\circ$}
 % Add more as you need them (shouldn't happen often).
@@
 \begin{abstract}
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Praesent convallis orci arcu, eu mollis dolor.
-Aliquam eleifend suscipit lacinia.
-Maecenas quam mi, porta ut lacinia sed, convallis ac dui.
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Suspendisse potenti.
+Coinduction allows programming and reasoning with possibly nonterminating programs and potentially infinite objects.
+In this paper, we compare two approaches for extending type theory with coinduction and coinductive types.
+More specifically, we show that guarded recursion and guarded recursive types can be simulated with sized types.
+We do this by defining a model of guarded recursion in type theory extended with sized types.
+The model is variation of the topos of trees, and it is formalized in Agda.
 \end{abstract}
@@
 
-\section{Preliminaries}
+\section{The Host Type Theory}
 \label{sec:prelim}
@@
 \input{Presheaves/Const}
-
 \input{Presheaves/Exp}
 
-\subsection{Modelling Simple Type Theory}
+\subsection{Modelling Simple Types}
 %\label{sec:kripke}
@@
 We start by defining clock quantification and the later modality, and how to construct terms of those types.
-In addition, we define the fixpoint combinator.
-We end this section by giving a type former for guarded recursive types.
+With this in place, we define the fixpoint combinator.
+In the end, we give the type former for guarded recursive types.
 

### 2019-01-28 code-oneclock-paper/latex/paper.tex
working on Sec 4

@@
 \newcommand{\GTT}{\textbf{GTT}}
+\newcommand{\Set}{\mathbf{Set}}
 
@@
 
-Next we define categorical semantics for the syntax defined in \Cref{sec:syntax}.
-To do so, we use a similar method as used by M{\o}gelberg \cite{Mogelberg14}.
-The interpretation of types depend on the clock contexts.
-If the clock context is empty, then types become sets.
-If the clock context has one clock, then types are interpreted as objects in the topos of trees.
+Next we give a categorical semantics for the calculus introduced in
+\Cref{sec:syntax}.  We take inspiration from M{\o}gelberg's model
+\cite{Mogelberg14}, where a (simple) type in a clock context
+containing $n$ clocks is interpreted
+as a presheaf in $\Set^{(\omega^n)^{\text{op}}}$, where $\omega$ is
+the preorder of ordered natural numbers. In our model we replace the
+category $\omega$ with the preorder of sizes. Moreover we only
+consider the cases where either the clock context is empty or it
+contains exactly one clock. This means that a type in \GTT\ is either
+interpreted as an element of \F{Set} or as a presheaf over \F{Size}. 
+In this section we show how to implement presheaves and how to model
+the fragment of \GTT\ corresponding to simply typed lambda
+calculus. The interpretation of the guarded recursive and coinductive
+features of \GTT\ is given in Section \ref{sec:guarded}.
+%% interpreted a $n = 0$ or $n = 1$. where Since in \GTT\
+%% every 
+%% consider clock contexts containing at most one clock.
+%% The type
+%% \AD{ClockCtx}  of syntactic clock contexts is also used for semantic clock contexts.
+%% 
+%% 
+%% 
+%% a variation of the topos of
+%% trees, where as the indexing category we replace the category of
+%% ordered natural numbers with the preorder of sizes.
+%% 
+%% he similar to To do so, we use a similar method as used by M{\o}gelberg \cite{Mogelberg14}.
+%% The interpretation of types depend on the clock contexts.
+%% If the clock context is empty, then types become sets.
+%% If the clock context has one clock, then types are interpreted as objects in the topos of trees.
 
@@
 \input{CloTT/Structure/Contexts}
-
 \input{CloTT/Structure/Types}
-
 \input{CloTT/Structure/Terms}
-
 \input{CloTT/Structure/Subst}
-
 \input{CloTT/Structure/DefinitionalEquality}
-
 \input{CloTT/Structure/ContextOperations}

### 2019-01-29 code-oneclock-paper/latex/Introduction.tex
Rewriting
Some rewriting (Sections 1-4)

@@
 language that underlies the deductive system of proof assistants such
-as Coq, Agda and Lean.  It is a total language,
+as Coq, Agda, and Lean \cite{norell}.  It is a total language,
 meaning that every program definable inside type theory is necessarily
@@
 coinductive types. Recursively defined elements of these types
-are required to be productive \cite{Coquand93} in the sense that every
-finite unfolding can be computed in a finite number of steps.
+are required to be productive in the sense that every
+finite unfolding can be computed in a finite number of steps \cite{Coquand93}.
 In Agda's encoding of coinductive types using ``musical notation''
@@
 at the level of types: sized types and guarded recursion. A sized type
-\cite{Hughes96} is a type annotated with the number of unfolding that
-elements of this type can undergo. Sized types have been implemented
-in Agda \cite{A-sized,AVW-normalization} and can be used in
+ is a type annotated with the number of unfolding that
+elements of this type can undergo \cite{Hughes96}. Sized types have been implemented
+in Agda and can be used in
 combination with coinductive records to specify
-coinductive types \cite{Copatterns}.  Guarded recursion \cite{Nakano}
+coinductive types \cite{Copatterns,AVW-normalization,norell}.  Guarded recursion \cite{Nakano}
 is a different approach where the type system is enhanced with a
@@
 streams satisfying the isomorphism \F{Str} \Ar{A} \F{≃} \Ar{A} \F{×}
-\IC{▻} (\F{Str} \F{A}). The tail of a guarded stream is available only
+\IC{▻} (\F{Str} \Ar{A}). The tail of a guarded stream is available only
 one time step ahead from now, as evidenced by the application of the
-later modality to \F{Str} \F{A}. Coinductive types can be constructed
+later modality to \F{Str} \Ar{A}. Coinductive types can be constructed
 from guarded recursive types in type theories that additionally
@@
 guarded variant of lambda calculus extended with a \IC{□} operation,
-which they call ``constant'' .  Our object calculus differs from
+which they call ``constant''.  Our object calculus differs from
 theirs in that our judgments are indexed by a clock context, which can
@@
 extracted from a literate Agda file, which implies that all the
-displayed code has passed Agda's type-check.
+displayed code has passed Agda's type and termination checker.
 

### 2019-01-29 code-oneclock-paper/latex/paper.tex
Some rewriting (Sections 1-4)

@@
 \newcommand{\GTT}{\textbf{GTT}}
+\newcommand{\AM}{\textbf{AM}}
 \newcommand{\Set}{\mathbf{Set}}
@@
 \input{CloTT/Structure/DefinitionalEquality}
-\input{CloTT/Structure/ContextOperations}
 
-Lastly, we use operations on sets and presheaves to define the type operators in simple type theory.
-For sets, we use products, sums, and function types in Agda.
-Products, sums, and exponentials of presheaves are interpreted with the operations in \Cref{sec:presheaves}.
-We only give the notation for function types.
-
+To interpret simple type theory, we also need to give the context operations, simple type formers, and operations on substitutions.
+Since their definitions are standard, we do not discuss them formally.
+For each of them, we need to make a case distinction based on the clock context.
+For example, the empty context is interpreted by the unit type and terminal presheaf depending on the clock context.
+We use the operations on presheaves defined in \Cref{sec:presheaves} to interpret simple type formers.
 \input{CloTT/TypeFormers/FunctionType}

### 2019-01-29 code-oneclock-paper/latex/paper.tex
minor changes in Sec 4

@@
 
-To interpret simple type theory, we also need to give the context operations, simple type formers, and operations on substitutions.
-Since their definitions are standard, we do not discuss them formally.
+We also need to provide a semantic version of 
+%To interpret simple type theory, we also need to give 
+the context operations, the simple type formers and the operations on substitutions.
+Since their definitions are standard, we do not discuss them in detail.
 For each of them, we need to make a case distinction based on the clock context.
-For example, the empty context is interpreted by the unit type and terminal presheaf depending on the clock context.
+For example, the empty variable context \IC{•} is interpreted either as the unit type
+or as the terminal presheaf, depending on the clock context.
 We use the operations on presheaves defined in \Cref{sec:presheaves} to interpret simple type formers.

### 2019-01-29 code-oneclock-paper/latex/Introduction.tex
Norell citation in intro

@@
 language that underlies the deductive system of proof assistants such
-as Coq, Agda, and Lean \cite{norell}.  It is a total language,
+as Coq, Agda \cite{norell} and Lean.  It is a total language,
 meaning that every program definable inside type theory is necessarily
@@
 combination with coinductive records to specify
-coinductive types \cite{Copatterns,AVW-normalization,norell}.  Guarded recursion \cite{Nakano}
+coinductive types \cite{Copatterns,AVW-normalization}.  Guarded recursion \cite{Nakano}
 is a different approach where the type system is enhanced with a

### 2019-01-29 code-oneclock-paper/latex/paper.tex
polished Section 5.1

@@
 \Cref{sec:syntax}.  We take inspiration from M{\o}gelberg's model
-\cite{Mogelberg14}, where a (simple) type in a clock context
+\cite{Mogelberg14} in which a (simple) type in a clock context
 containing $n$ clocks is interpreted
@@
 \label{sec:guarded}
-Now we have the simple type formers and their terms.
-The next step is to add the type formers required for guarded recursion.
-We start by defining clock quantification and the later modality, and how to construct terms of those types.
-With this in place, we define the fixpoint combinator.
-In the end, we give the type former for guarded recursive types.
+In this section we add the guarded
+recursive and coinductive features to the denotational semantics.
+%Now we have the simple type formers and their terms.
+%The next step is to add the type formers required for guarded recursion.
+We start by defining the semantic box modality together with its
+introduction and elimination rule. Then we construct the semantic
+later modality. We show how to define the fixpoint combinator and the
+force operation using sized types. In the end we discuss how to model
+guarded recursive types.
+%% introduce the
+%% semantic 
+%%  together with the
+%% terms associated 
+%% and how to construct terms of those types.
+%% With this in place, we define the fixpoint combinator.
+%% In the end, we give the type former for guarded recursive types.
 
-\subsection{Context Weakening and Clock Quantification}
+\subsection{Context Weakening and the Box Modality}
 \input{CloTT/TypeFormers/WeakenClock}

### 2019-01-29 code-oneclock-paper/latex/paper.tex
rewrote 5.1 minorly

@@
 \label{sec:guarded}
-In this section we add the guarded
+In this section, we add the required guarded
 recursive and coinductive features to the denotational semantics.
@@
 later modality. We show how to define the fixpoint combinator and the
-force operation using sized types. In the end we discuss how to model
+force operation using sized types. In the end, we discuss how to model
 guarded recursive types.

### 2019-01-31 code-oneclock-paper/latex/Introduction.tex
Added overview of paper

@@
 
+The remainder is organized as follows.
+We discuss the meta-theory and recall sized types in \Cref{sec:prelim}.
+Then we give the syntax of guarded recursive type theory \Cref{sec:syntax}.
+In \Cref{sec:presheaf_sem,sec:guarded}, we define a denotational semantics of the syntax using sized types.  
+For that, we first define a presheaf model and give the Kripke semantics, and then we show how to interpret the additional type and term formers of guarded recursive type theory.
+Finally, we conclude that the syntax is consistent in \Cref{sec:consistent}.
+
 %\NV{WIP from this point}

### 2019-01-31 code-oneclock-paper/latex/Introduction.tex
Added references

@@
 language that underlies the deductive system of proof assistants such
-as Coq, Agda \cite{norell} and Lean.  It is a total language,
+as Coq, Agda, and Lean \cite{barras1997coq,de2015lean,norell}. It is a total language,
 meaning that every program definable inside type theory is necessarily
@@
 the application of a constructor. A similar syntactic
-check is employed in Coq.
+check is employed in Coq \cite{DBertotK08}.
 This restriction

### 2019-02-01 code-oneclock-paper/latex/Introduction.tex
conclusions and overview

--- 2019-01-29 code-oneclock-paper/latex/Introduction.tex
@@
 \cite{atkey2013productive,BahrGM17}. Currently there is no
-implementation of a calculus with guarded recursion.
+implementation of a calculus for guarded recursion.
 %%  nor guarded recursion
@@
 \cite{AltenkirchK16,Chapman09}, we present an Agda formalization of
-the syntax of a simple type theory with guarded recursion. This object
+the syntax of a simple type theory for guarded recursion. This object
 language, which we call \GTT, is a variant of Atkey and McBride's type
@@
 
-Abel and Vezzosi \cite{AbelV14} also formalized a simple type theory
-extended with the later modality in Agda. They focus on operational
-properties of the calculus and give a certified proof of strong
-normalization. In our work we consider a richer type system and we
-formalize its denotational semantics in Agda. Nevertheless, we do not
-investigate the dynamic behaviour of our calculus, which we leave to
-future work.
-
-%% A detailed account of how to model the characteristic features of
-%% \GTT, consisting of the \IC{▻} and
-%% \IC{□}  modality together with guarded recursive types, is given in
-%% Section \ref{sec:guarded}.
+%%Abel and Vezzosi \cite{AbelV14} also formalized a simple type theory
+%%extended with the later modality in Agda. They focus on operational
+%%properties of the calculus and give a certified proof of strong
+%%normalization. In our work we consider a richer type system and we
+%%formalize its denotational semantics in Agda. Nevertheless, we do not
+%%investigate the dynamic behaviour of our calculus, which we leave to
+%%future work.
 
@@
 \begin{enumerate}
-  \item We formalize syntax and semantics of a type theory with
+  \item We formalize syntax and semantics of a type theory for
     guarded recursion in Agda. This is the first such denotational model developed using an extension of Martin-L\"of intensional
@@
   recursion crucially requires the employment of sized types. This shows that
-  guarded recursive types can be reduced to sized types and
+  guarded recursion can be reduced to sized types and
   constitutes a stepping stone towards a clear understanding of  the connections
@@
 displayed code has passed Agda's type and termination checker.
+
+The material is organized in the following way.
+In \Cref{sec:prelim}, we discuss the metatheory and we give an
+overview of sized types.
+In \Cref{sec:syntax}, we introduce the syntax of \GTT, our object type theory for guarded recursion.
+Subsequently, we give a categorical semantics.
+In \Cref{sec:presheaf_sem}, we show how to implement presheaves over
+sizes and how to model the fragment of
+\GTT\ corresponding to simply typed lambda calculus.
+In \Cref{sec:guarded}, we discuss the semantics of the guarded
+recursive and coinductive features.
+In \Cref{sec:consistent}, we describe how to formally interpret the
+syntax into the model, which entails the consistency of the syntax.
+Finally, in \Cref{sec:concl}, we draw conclusions and suggest  future
+directions of work.
+
+%% give the Kripke semantics
+%%\GTT.
+%%For that, we first define a presheaf model and give the Kripke semantics, and then we show how to interpret the additional type and term formers of guarded recursive type theory.
+%%Finally, we conclude that the syntax is consistent in \Cref{sec:consistent}.
 

### 2019-02-01 code-oneclock-paper/latex/paper.tex
Sec 5.2 until line 429
Added overview of paper
Added a unicode symbol for ▸
conclusions and overview

@@
 \newunicodechar{∁}{$\mathbb{C}$}
+\newunicodechar{▸}{$\blacktriangleright$}
 \newunicodechar{►}{$\blacktriangleright$}
@@
 \subsection{Modelling Simple Types}
-%\label{sec:kripke}
+\label{sec:kripke}
 \input{CloTT/Structure/Contexts}
@@
 
-\subsection{Guarded Recursive Types}
+\subsection
+{Guarded Recursive Types}
+\label{sec:grt}
 \input{CloTT/TypeFormers/Mu}
@@
 \section{Consistency}
+\label{sec:consistent}
 \input{GuardedTT}
 
-\section{Conclusion}
-We formally defined a syntax of guarded type theory with explicit substitutions and weakening, and we constructed denotational semantics for it in type theory extended with sized types.
+\section{Conclusions and Future Work}
+\label{sec:concl}
+We presented a simple type theory for guarded recursion that we called \GTT. We
+formalized its syntax and semantics in Agda. Crucially, sized types
+were employed for giving an interpretation to the characteristic
+features of guarded recursion. From this we conclude that guarded
+recursion can be simulated using sized types. We greatly benefited
+of the fact that sized types constitute a native feature of Agda, so
+we were able to fully develop our theory inside a proof assistent.
+
+This work can be extended is several different directions.
+
+Various type theories for guarded recursion in the literature include
+dependent types. Currently, there exist two disciplines for mixing
+dependent types with guarded recursion: delayed substitutions
+\cite{bizjak2016guarded} and ticks \cite{BahrGM17}. We plan to extend
+the syntax and semantics of \GTT\ with dependent types following one
+of these two disciplines.
+
+Abel and Vezzosi \cite{AbelV14} formalized a simple type theory
+extended with the later modality in Agda. They focus on operational
+properties of the calculus and give a certified proof of strong
+normalization. In future work, we plan to investigate the metatheory
+and the dynamic behaviour of \GTT, for example by formalizing a  type
+checker and a normalization algorithm.
+
+\remove{
+and weakening, and we constructed denotational semantics for it in type theory extended with sized types.
 From this, we concluded that this theory is consistent and that guarded recursion can be defined via sized types.
@@
 Second of all, with the deep embedding in place, one can further study the meta-theory by defining a formalized type checking and a normalization algorithm.
+}
+
+Finally, we want to understand weather it is possible to reduce sized types to guarded
+recursion.  This does not seems directly doable, since sizes are not uniquely employed with coinductive types as a
+tool for easing the productivity check of corecursive
+definitions, but they are also used as auxiliary arguments of inductive
+types for facilitating the termination check of recursive
+definitions. It seems that the existing type theories for guarded
+recursion are not capable of capturing this dual aspect of sizes.
 

### 2019-02-01 code-oneclock-paper/latex/Introduction.tex
trying to cut

@@
 language that underlies the deductive system of proof assistants such
-as Coq, Agda, and Lean \cite{barras1997coq,de2015lean,norell}. It is a total language,
+as Agda and Coq \cite{norell,barras1997coq}. It is a total language,
 meaning that every program definable inside type theory is necessarily

### 2019-02-01 code-oneclock-paper/latex/paper.tex
trying to cut
text changes

@@
 This work can be extended is several different directions.
-
 Various type theories for guarded recursion in the literature include
@@
 dependent types with guarded recursion: delayed substitutions
-\cite{bizjak2016guarded} and ticks \cite{BahrGM17}. We plan to extend
+\cite{bizjak2016guarded} and ticks \cite{BahrGM17}. It would be interesting to extend
 the syntax and semantics of \GTT\ with dependent types following one
-of these two disciplines.
+of these methods.
 
@@
 properties of the calculus and give a certified proof of strong
-normalization. In future work, we plan to investigate the metatheory
-and the dynamic behaviour of \GTT, for example by formalizing a  type
+normalization. As future work, we plan to investigate the metatheory
+and the dynamic behaviour of \GTT\ by formalizing a  type
 checker and a normalization algorithm.
@@
 
-Finally, we want to understand weather it is possible to reduce sized types to guarded
-recursion.  This does not seems directly doable, since sizes are not uniquely employed with coinductive types as a
-tool for easing the productivity check of corecursive
-definitions, but they are also used as auxiliary arguments of inductive
-types for facilitating the termination check of recursive
-definitions. It seems that the existing type theories for guarded
-recursion are not capable of capturing this dual aspect of sizes.
-
+Finally, we want to understand weather it is possible to reduce sized
+types to guarded recursion.  This does not seems directly doable,
+since sizes are not uniquely employed with coinductive types as a tool
+for easing the productivity check of corecursive definitions, but they
+are also used as auxiliary arguments of inductive types for
+facilitating the termination check of recursive definitions. It seems
+that, in order to capture this dual aspect of sizes, one needs to
+extend the existing type theories for guarded recursion with
+additional features.
 %%

### 2019-02-01 code-oneclock-paper/latex/paper.tex
abstract

@@
 \begin{abstract}
-Coinduction allows programming and reasoning with possibly nonterminating programs and potentially infinite objects.
-In this paper, we compare two approaches for extending type theory with coinduction and coinductive types.
-More specifically, we show that guarded recursion and guarded recursive types can be simulated with sized types.
-We do this by defining a model of guarded recursion in type theory extended with sized types.
-The model is variation of the topos of trees, and it is formalized in Agda.
+  In type theory, programming and reasoning with possibly
+  non-terminating programs and potentially infinite objects is
+  achieved using coinductive types. Crucially, recursively defined
+  programs of coinductive types are required to be productive. Proof
+  assistants such as Agda and Coq traditionally employ strict syntactic
+  productivity checks, which commonly make programming with coinductive types
+  convoluted. One way to overcome this issue is by encoding productivity at
+  the level of types, so that the type system forbids the
+  implementation of non-productive corecursive programs.
+%%, meaning
+%%  that although their definitions can be unfolded \emph{ad infinitum},
+%%  finite unfoldings are guaranteed to produce . 
+  In this paper we compare two different approaches to type-based
+  productivity: guarded recursion and sized types. More specifically,
+  we show how to simulate guarded recursion in Agda using sized
+  types. First we formalize the syntax of a simple type theory for
+  guarded recursion, corresponding to a variant of Atkey and McBride's
+  type system for productive coprogramming
+  \cite{atkey2013productive}. Then we give a denotational semantics
+  using presheaves over the preorder of sizes. Sized types are
+  fundamentally employed in the interpretation of the characteristic
+  features of guarded recursion, notably the fixpoint combinator.
+%%extending type theory with
+%%  coinduction and coinductive types.  More specifically, we show that
+%%  guarded recursion and guarded recursive types can be simulated with
+%%  sized types.  We do this by defining a model of guarded recursion in
+%%  type theory extended with sized types.  The model is variation of
+%%  the topos of trees, and it is formalized in Agda.
 \end{abstract}
@@
 
-This work can be extended is several different directions.
+This work can be extended in several different directions.
 Various type theories for guarded recursion in the literature include

### 2019-02-03 code-oneclock-paper/latex/paper.tex
Chages in abstract

@@
   non-terminating programs and potentially infinite objects is
-  achieved using coinductive types. Crucially, recursively defined
-  programs of coinductive types are required to be productive. Proof
-  assistants such as Agda and Coq traditionally employ strict syntactic
-  productivity checks, which commonly make programming with coinductive types
-  convoluted. One way to overcome this issue is by encoding productivity at
+  achieved with coinductive types. Recursively defined
+  programs using such types need to be productive to guarantee consistency, and proof
+  assistants such as Agda and Coq use syntactic
+  productivity checks for that.
+  However, this convolutes programs with coinductive types.
+
+  One way to overcome this issue, is by encoding productivity at
   the level of types, so that the type system forbids the
@@
 %%  finite unfoldings are guaranteed to produce . 
-  In this paper we compare two different approaches to type-based
-  productivity: guarded recursion and sized types. More specifically,
+  In this paper, we compare two such approaches: guarded recursion and sized types. More specifically,
   we show how to simulate guarded recursion in Agda using sized
-  types. First we formalize the syntax of a simple type theory for
-  guarded recursion, corresponding to a variant of Atkey and McBride's
-  type system for productive coprogramming
-  \cite{atkey2013productive}. Then we give a denotational semantics
-  using presheaves over the preorder of sizes. Sized types are
-  fundamentally employed in the interpretation of the characteristic
-  features of guarded recursion, notably the fixpoint combinator.
+  types. We formalize the syntax of a simple type theory for
+  guarded recursion, which is a variant of Atkey and McBride's
+  type system for productive coprogramming. Then we give a denotational semantics
+  using presheaves over the preorder of sizes. 
+%Sized types are fundamentally employed in the interpretation of the characteristic features of guarded recursion, notably the fixpoint combinator.
 %%extending type theory with

### 2019-02-03 code-oneclock-paper/latex/Introduction.tex
Rewrites in introduction

@@
 language that underlies the deductive system of proof assistants such
-as Agda and Coq \cite{norell,barras1997coq}. It is a total language,
+as Agda and Coq \cite{barras1997coq,norell}. It is a total language,
 meaning that every program definable inside type theory is necessarily
@@
 Possibly non-terminating computations
-and infinite structures such as non-wellfounded trees can be
+and infinite structures, such as non-wellfounded trees, can be
 represented in type theory by extending the type system with
 coinductive types. Recursively defined elements of these types
-are required to be productive in the sense that every
+need to be productive in the sense that every
 finite unfolding can be computed in a finite number of steps \cite{Coquand93}.
@@
 \cite{DA10}, productivity is enforced via a strict obligation: in the
-definition of a corecursive function, the recursive
-call is required to appear directly under
+definition of a corecursive function, recursive
+calls must appear directly under
 the application of a constructor. A similar syntactic
-check is employed in Coq \cite{DBertotK08}.
+check is used in Coq \cite{DBertotK08}.
 This restriction
 typically makes programming with coinductive types cumbersome,
-which spawned the search for alternative techniques for ensuring the
+which spawned the search for alternative techniques to ensure the
 well-definedness of corecursive definitions.

### 2019-02-03 code-oneclock-paper/latex/paper.tex
Fixes in Section 4

@@
 as a presheaf in $\Set^{(\omega^n)^{\text{op}}}$, where $\omega$ is
-the preorder of ordered natural numbers. In our model we replace the
-category $\omega$ with the preorder of sizes. Moreover we only
+the preorder of ordered natural numbers. In our model, we replace the
+category $\omega$ with the preorder of sizes. Moreover, we only
 consider the cases where either the clock context is empty or it
@@
 interpreted as an element of \F{Set} or as a presheaf over \F{Size}. 
-In this section we show how to implement presheaves and how to model
+In this section, we show how to implement presheaves and how to model
 the fragment of \GTT\ corresponding to simply typed lambda
@@
 For example, the empty variable context \IC{•} is interpreted either as the unit type
-or as the terminal presheaf, depending on the clock context.
+or as the terminal presheaf depending on the clock context.
 We use the operations on presheaves defined in \Cref{sec:presheaves} to interpret simple type formers.

### 2019-02-03 code-oneclock-paper/latex/paper.tex
Fixes in conclusion

@@
 We presented a simple type theory for guarded recursion that we called \GTT. We
-formalized its syntax and semantics in Agda. Crucially, sized types
-were employed for giving an interpretation to the characteristic
-features of guarded recursion. From this we conclude that guarded
+formalized its syntax and semantics in Agda. Sized types
+were employed to interpret the characteristic
+features of guarded recursion. From this, we conclude that guarded
 recursion can be simulated using sized types. We greatly benefited
@@
 Various type theories for guarded recursion in the literature include
-dependent types. Currently, there exist two disciplines for mixing
-dependent types with guarded recursion: delayed substitutions
+dependent types. Currently, there are two disciplines for these two features: delayed substitutions
 \cite{bizjak2016guarded} and ticks \cite{BahrGM17}. It would be interesting to extend
@@
 
-Finally, we want to understand weather it is possible to reduce sized
+Finally, we want to understand whether it is possible to reduce sized
 types to guarded recursion.  This does not seems directly doable,
@@
 facilitating the termination check of recursive definitions. It seems
-that, in order to capture this dual aspect of sizes, one needs to
-extend the existing type theories for guarded recursion with
-additional features.
+that, in order to capture this dual aspect of sizes, one %needs to
+%extend the existing type theories for guarded recursion with
+%additional features.
 %%

### 2019-02-03 code-oneclock-paper/latex/paper.tex
Sec 6 title

--- 2019-02-03 code-oneclock-paper/latex/paper.tex
@@
   non-terminating programs and potentially infinite objects is
-  achieved with coinductive types. Recursively defined
-  programs using such types need to be productive to guarantee consistency, and proof
-  assistants such as Agda and Coq use syntactic
-  productivity checks for that.
-  However, this convolutes programs with coinductive types.
-
-  One way to overcome this issue, is by encoding productivity at
+  achieved using coinductive types. Crucially, recursively defined
+  programs of coinductive types are required to be productive. Proof
+  assistants such as Agda and Coq traditionally employ strict syntactic
+  productivity checks, which commonly make programming with coinductive types
+  convoluted. One way to overcome this issue is by encoding productivity at
   the level of types, so that the type system forbids the
@@
 %%  finite unfoldings are guaranteed to produce . 
-  In this paper, we compare two such approaches: guarded recursion and sized types. More specifically,
+  In this paper we compare two different approaches to type-based
+  productivity: guarded recursion and sized types. More specifically,
   we show how to simulate guarded recursion in Agda using sized
-  types. We formalize the syntax of a simple type theory for
-  guarded recursion, which is a variant of Atkey and McBride's
-  type system for productive coprogramming. Then we give a denotational semantics
-  using presheaves over the preorder of sizes. 
-%Sized types are fundamentally employed in the interpretation of the characteristic features of guarded recursion, notably the fixpoint combinator.
+  types. First we formalize the syntax of a simple type theory for
+  guarded recursion, corresponding to a variant of Atkey and McBride's
+  type system for productive coprogramming
+  \cite{atkey2013productive}. Then we give a denotational semantics
+  using presheaves over the preorder of sizes. Sized types are
+  fundamentally employed in the interpretation of the characteristic
+  features of guarded recursion, notably the fixpoint combinator.
 %%extending type theory with
@@
 
-\section{Consistency}
+\section{Interpretation and Consistency}
 \label{sec:consistent}

### 2019-02-03 code-oneclock-paper/latex/Introduction.tex
127-128

@@
 combination with coinductive records to specify
-coinductive types \cite{Copatterns,AVW-normalization}.  Guarded recursion \cite{Nakano}
+coinductive types \cite{Copatterns,AVW-normalization}, as exemplified
+by Abel and Chapman's work \cite{AC14}.  Guarded recursion \cite{Nakano}
 is a different approach where the type system is enhanced with a

### 2019-02-03 code-oneclock-paper/latex/paper.tex
127-128

--- 2019-02-03 code-oneclock-paper/latex/paper.tex
@@
   non-terminating programs and potentially infinite objects is
-  achieved with coinductive types. Recursively defined
-  programs using such types need to be productive to guarantee consistency, and proof
-  assistants such as Agda and Coq use syntactic
-  productivity checks for that.
-  However, this convolutes programs with coinductive types.
-
-  One way to overcome this issue, is by encoding productivity at
-  the level of types, so that the type system forbids the
-  implementation of non-productive corecursive programs.
+  achieved using coinductive types. Recursively defined programs of
+  these types are required to be productive to guarantee the
+  consistency of the type system. Proof assistants such as Agda and
+  Coq traditionally employ strict syntactic productivity checks, which
+  commonly make programming with coinductive types convoluted.  One
+  way to overcome this issue is by encoding productivity at the level
+  of types, so that the type system forbids the implementation of
+  non-productive corecursive programs.
 %%, meaning
@@
 %%  finite unfoldings are guaranteed to produce . 
-  In this paper, we compare two such approaches: guarded recursion and sized types. More specifically,
+  In this paper we compare two different approaches to type-based
+  productivity: guarded recursion and sized types. More specifically,
   we show how to simulate guarded recursion in Agda using sized
-  types. We formalize the syntax of a simple type theory for
-  guarded recursion, which is a variant of Atkey and McBride's
-  type system for productive coprogramming. Then we give a denotational semantics
-  using presheaves over the preorder of sizes. 
+  types. We formalize the syntax of a simple type theory for guarded
+  recursion, corresponding to a variant of Atkey and McBride's
+  calculus for productive coprogramming
+  \cite{atkey2013productive}. Then we give a denotational semantics
+  using presheaves over the preorder of sizes. Sized types are
+  fundamentally employed in the interpretation of the characteristic
+  features of guarded recursion, notably the fixpoint combinator.
 %Sized types are fundamentally employed in the interpretation of the characteristic features of guarded recursion, notably the fixpoint combinator.
@@
 facilitating the termination check of recursive definitions. It seems
-that, in order to capture this dual aspect of sizes, one %needs to
-%extend the existing type theories for guarded recursion with
-%additional features.
+that, in order to capture this dual aspect of sizes, one needs to
+extend the existing type theories for guarded recursion with
+additional features.
 %%

### 2019-02-03 code-oneclock-paper/latex/Introduction.tex
Small change in intro

@@
 coinductive types \cite{Copatterns,AVW-normalization}, as exemplified
-by Abel and Chapman's work \cite{AC14}.  Guarded recursion \cite{Nakano}
+by Abel and Chapman's work \cite{AC14}.
+
+Guarded recursion \cite{Nakano}
 is a different approach where the type system is enhanced with a
@@
 programming with productive recursive functions and allows the
-specification of guarded recursive types, \eg the type of guarded
+specification of guarded recursive types.
+These types can be used in combination with clock quantification to define  coinductive types \cite{atkey2013productive,BahrGM17}. Currently there is no
+implementation of a calculus for guarded recursion.
+\remove{, \eg the type of guarded
 streams satisfying the isomorphism \F{Str} \Ar{A} \F{≃} \Ar{A} \F{×}
@@
 \cite{atkey2013productive,BahrGM17}. Currently there is no
-implementation of a calculus for guarded recursion.
+implementation of a calculus for guarded recursion.}
 %%  nor guarded recursion

### 2019-02-04 code-oneclock-paper/latex/paper.tex
Definitional equality in different paragraph
Different version of conclusion

@@
 \input{CloTT/Structure/Subst}
-\input{CloTT/Structure/DefinitionalEquality}
+%\input{CloTT/Structure/DefinitionalEquality}
 
@@
 
+\remove{
 Finally, we want to understand whether it is possible to reduce sized
@@
 additional features.
+}
+
+Finally, we would like to understand whether sized types can be simulated using guarded recursion.
+The difficulty is representing coinductive types.
+One could represent sizes by the conatural numbers, but this might not be sufficient to model infinitary coinductive types.
 %%

### 2019-02-04 code-oneclock-paper/latex/paper.tex
Minor textual changes in abstract

@@
   achieved using coinductive types. Recursively defined programs of
-  these types are required to be productive to guarantee the
+  these types need to be productive to guarantee the
   consistency of the type system. Proof assistants such as Agda and
@@
   types. We formalize the syntax of a simple type theory for guarded
-  recursion, corresponding to a variant of Atkey and McBride's
+  recursion, which is a variant of Atkey and McBride's
   calculus for productive coprogramming
@@
   using presheaves over the preorder of sizes. Sized types are
-  fundamentally employed in the interpretation of the characteristic
+  fundamentally used to interpret the characteristic
   features of guarded recursion, notably the fixpoint combinator.

### 2019-02-04 code-oneclock-paper/latex/paper.tex
Modified conclusion

@@
 Finally, we would like to understand whether sized types can be simulated using guarded recursion.
-The difficulty is representing coinductive types.
-One could represent sizes by the conatural numbers, but this might not be sufficient to model infinitary coinductive types.
+Sized types require dependent types and subtyping, which \GTT\ does not have.
+We conjecture that Clocked Type Theory \cite{BahrGM17} can model sized types with explicit subtyping.
 %%

### 2019-02-04 code-oneclock-paper/latex/paper.tex
minor fixes in abstract

@@
   way to overcome this issue is by encoding productivity at the level
-  of types, so that the type system forbids the implementation of
+  of types so that the type system forbids the implementation of
   non-productive corecursive programs.
@@
 %%  finite unfoldings are guaranteed to produce . 
-  In this paper we compare two different approaches to type-based
+  In this paper, we compare two different approaches to type-based
   productivity: guarded recursion and sized types. More specifically,
@@
   recursion, which is a variant of Atkey and McBride's
-  calculus for productive coprogramming
-  \cite{atkey2013productive}. Then we give a denotational semantics
+  calculus for productive coprogramming. Then we give a denotational semantics
   using presheaves over the preorder of sizes. Sized types are

### 2019-02-04 code-oneclock-paper/latex/paper.tex
Removed a comma
consistency
Changes in sec 6
behavior

@@
 %%  finite unfoldings are guaranteed to produce . 
-  In this paper, we compare two different approaches to type-based
+  In this paper we compare two different approaches to type-based
   productivity: guarded recursion and sized types. More specifically,
@@
 \section{Categorical Semantics}
+\label{sec:presheaf_sem}
 
@@
 
-\label{sec:presheaf_sem}
 \subsection{Presheaves}
@@
 \label{sec:consistent}
+\input{Prelude/Interpretation}
+\input{CloTT/InterpretSyntax}
 \input{GuardedTT}
+
+%\section{Interpretation and Consistency}
+%\input{GuardedTTAlt}
 
@@
 normalization. As future work, we plan to investigate the metatheory
-and the dynamic behaviour of \GTT\ by formalizing a  type
+and the dynamic behavior of \GTT\ by formalizing a  type
 checker and a normalization algorithm.

### 2019-02-06 code-oneclock-paper/latex/paper.tex
Rasmus

@@
 recursion can be simulated using sized types. We greatly benefited
-of the fact that sized types constitute a native feature of Agda, so
+from the fact that sized types constitute a native feature of Agda, so
 we were able to fully develop our theory inside a proof assistent.

### 2019-02-07 code-oneclock-paper/latex/Introduction.tex
fixes in Sec 3

@@
 language that underlies the deductive system of proof assistants such
-as Agda and Coq \cite{barras1997coq,norell}. It is a total language,
+as Agda \cite{norell} and Coq \cite{barras1997coq}. It is a total language,
 meaning that every program definable inside type theory is necessarily
@@
 specification of guarded recursive types.
-These types can be used in combination with clock quantification to define  coinductive types \cite{atkey2013productive,BahrGM17}. Currently there is no
+These types can be used in combination with clock quantification to define  coinductive types \cite{atkey2013productive,bizjak2016guarded,BahrGM17}. Currently there is no
 implementation of a calculus for guarded recursion.
@@
 which the clock context can contain at most one clock. The types of
-\GTT\ include the aformentioned \IC{▻} modality and a \IC{□} modality,
+\GTT\ include the aforementioned \IC{▻} modality and a \IC{□} modality,
 a nameless analogue of Atkey and McBride's universal clock

### 2019-02-07 code-oneclock-paper/latex/paper.tex
gone through the paper

@@
 For example, the empty variable context \IC{•} is interpreted either as the unit type
-or as the terminal presheaf depending on the clock context.
+or as the terminal presheaf, depending on the state of the clock context.
 We use the operations on presheaves defined in \Cref{sec:presheaves} to interpret simple type formers.
@@
 Various type theories for guarded recursion in the literature include
-dependent types. Currently, there are two disciplines for these two features: delayed substitutions
+dependent types. Currently, there exist two disciplines for mixing
+dependent types with guarded recursion: delayed substitutions
 \cite{bizjak2016guarded} and ticks \cite{BahrGM17}. It would be interesting to extend
 the syntax and semantics of \GTT\ with dependent types following one
-of these methods.
+of these two methods.
 
@@
 and the dynamic behavior of \GTT\ by formalizing a  type
-checker and a normalization algorithm.
+checker and a normalization algorithm. This would also set up the
+basis for a usable implementation of \GTT.
 

### 2019-02-08 code-oneclock-paper/latex/paper.tex
6)

@@
 
-Finally, we would like to understand whether sized types can be simulated using guarded recursion.
-Sized types require dependent types and subtyping, which \GTT\ does not have.
-We conjecture that Clocked Type Theory \cite{BahrGM17} can model sized types with explicit subtyping.
+Finally, we would like to understand whether sized types can be
+simulated using guarded recursion.
+This could either be done by modeling sized types in a topos of
+trees-like category \cite{BMSS-synthetic,MannaaM18} or via the
+encoding of a type theory with sized types into a dependent type
+theory for guarded recursion such as Clocked Type Theory
+\cite{BahrGM17}. 
+%Sized types require dependent types and subtyping, which \GTT\ does not have.
+%We conjecture that Clocked Type Theory \cite{BahrGM17} can model sized types with explicit subtyping.
+
 %%

### 2019-02-11 code-oneclock-paper/latex/Introduction.tex
2)
minor changes until page 7

@@
 the application of a constructor. A similar syntactic
-check is used in Coq \cite{DBertotK08}.
+check is used in Coq. % \cite{DBertotK08}.
 This restriction
@@
 theirs in that our judgments are indexed by a clock context, which can
-be empty or containing exactly one clock. In this respect \GTT\ is
-closer in spirit to Atkey and McBride's language. The design of \GTT\
-also has the benefit of allowing a more appealing introduction rule for
+be empty or containing exactly one clock. 
+%In this respect \GTT\ is closer in spirit to Atkey and McBride's
+%language.
+The design of \GTT\ has the benefit of allowing a more appealing introduction rule for
 \IC{□} than Clouston et al.'s.
@@
 \url{https://github.com/niccoloveltri/agda-clott}. The formalization
-uses Agda 2.5.4.1 and Agda standard library 0.16. The paper is
+uses Agda 2.5.4.2 and Agda standard library 0.16. The paper is
 extracted from a literate Agda file, which implies that all the
@@
 recursive and coinductive features.
-In \Cref{sec:consistent}, we describe how to formally interpret the
-syntax into the model, which entails the consistency of the syntax.
+In \Cref{sec:consistent}, we prove the object language sound \wrt the
+categorical model,
+%describe how to formally interpret the syntax into the model, 
+which in turn entails the consistency of the syntax.
 Finally, in \Cref{sec:concl}, we draw conclusions and suggest  future

### 2019-02-11 code-oneclock-paper/latex/paper.tex
minor changes Sec 4

@@
 Since their definitions are standard, we do not discuss them in detail.
-For each of them, we need to make a case distinction based on the clock context.
-For example, the empty variable context \IC{•} is interpreted either as the unit type
-or as the terminal presheaf, depending on the state of the clock context.
+For each of them, we need to make a case distinction based on the
+state of the clock context.
+For example, the empty variable context \IC{•} is interpreted
+as the unit type in the clock context \IC{∅}, and it is interpreted as 
+the terminal presheaf in the clock context \IC{κ}.
+%, depending on the state of the clock context.
 We use the operations on presheaves defined in \Cref{sec:presheaves} to interpret simple type formers.

### 2019-02-27 code-oneclock-paper/types-abstract/abstract.tex
started types abstract

--- 2019-02-11 code-oneclock-paper/latex/Introduction.tex
@@
+% easychair.tex,v 3.5 2017/03/15
+
+\documentclass{easychair}
+%\documentclass[EPiC]{easychair}
+%\documentclass[EPiCempty]{easychair}
+%\documentclass[debug]{easychair}
+%\documentclass[verbose]{easychair}
+%\documentclass[notimes]{easychair}
+%\documentclass[withtimes]{easychair}
+%\documentclass[a4paper]{easychair}
+%\documentclass[letterpaper]{easychair}
+
+\usepackage{doc}
+
+% use this if you have a long article and want to create an index
+% \usepackage{makeidx}
+
+% In order to save space or manage large tables or figures in a
+% landcape-like text, you can use the rotating and pdflscape
+% packages. Uncomment the desired from the below.
+%
+% \usepackage{rotating}
+% \usepackage{pdflscape}
+
+% Some of our commands for this guide.
+%
+\newcommand{\easychair}{\textsf{easychair}}
+\newcommand{\miktex}{MiK{\TeX}}
+\newcommand{\texniccenter}{{\TeX}nicCenter}
+\newcommand{\makefile}{\texttt{Makefile}}
+\newcommand{\latexeditor}{LEd}
+
+\newcommand{\remove}[1]{}
+
+\newcommand{\ie}{\emph{i.e.,} }
+\newcommand{\cf}{\emph{c.f.} }
+\newcommand{\eg}{\emph{e.g.,} }
+\newcommand{\etal}{\emph{et~al.}}
+\newcommand{\etc}{\emph{etc.}}
+\newcommand{\wrt}{w.r.t.~}
+\newcommand{\resp}{resp.~}
+\newcommand{\loccit}{\emph{loc. cit.} }
+
+\newcommand{\GTT}{\textbf{GTT}}
+
+%\makeindex
+
+%% Front Matter
+%%
+% Regular title as in the article class.
+%
+\title{Guarded Recursion in Agda via Sized Type}
+
+% Authors are joined by \and. Their affiliations are given by \inst, which indexes
+% into the list defined using \institute
+%
+\author{
+Niccol\`o Veltri\inst{1}
+\and
+Niels van der Weide\inst{2}
+}
+
+% Institutes for affiliations are also joined by \and,
+\institute{
+  Department of Computer Science, IT
+  University of Copenhagen, Denmark \\
+  \email{nive@itu.dk}
+\and
+   Institute for Computation and Information Sciences, Radboud University, Nijmegen, The Netherlands \\
+   \email{nweide@cs.ru.nl}
+ }
+
+%  \authorrunning{} has to be set for the shorter version of the authors' names;
+% otherwise a warning will be rendered in the running heads. When processed by
+% EasyChair, this command is mandatory: a document without \authorrunning
+% will be rejected by EasyChair
+
+\authorrunning{Veltri and van der Weide}
+
+% \titlerunning{} has to be set to either the main title or its shorter
+% version for the running heads. When processed by
+% EasyChair, this command is mandatory: a document without \titlerunning
+% will be rejected by EasyChair
+\titlerunning{Guarded Recursion in Agda via Sized Types}
+
+\begin{document}
+
+\maketitle
+
 Dependent type theory is an expressive functional programming
@@
 is a different approach where the type system is enhanced with a
-modality, called ``later'' and written \IC{▻}, encoding time delay in
+modality, called ``later'' and written $\triangleright$, encoding time delay in
 types. The later modality comes with a general fixpoint combinator for
@@
 \remove{, \eg the type of guarded
-streams satisfying the isomorphism \F{Str} \Ar{A} \F{≃} \Ar{A} \F{×}
-\IC{▻} (\F{Str} \Ar{A}). The tail of a guarded stream is available only
+streams satisfying the isomorphism $\mathsf{Str} A \simeq A \times
+\triangleright (\mathsf{Str} A)$. The tail of a guarded stream is available only
 one time step ahead from now, as evidenced by the application of the
-later modality to \F{Str} \Ar{A}. Coinductive types can be constructed
+later modality to $\mathsf{Str} A$. Coinductive types can be constructed
 from guarded recursive types in type theories that additionally
@@
 which the clock context can contain at most one clock. The types of
-\GTT\ include the aforementioned \IC{▻} modality and a \IC{□} modality,
+\GTT\ include the aforementioned $\triangleright$ modality and a box modality,
 a nameless analogue of Atkey and McBride's universal clock
 quantification. Clouston \etal \cite{CloustonBGB15} studied a
-guarded variant of lambda calculus extended with a \IC{□} operation,
+guarded variant of lambda calculus extended with a box operation,
 which they call ``constant''.  Our object calculus differs from
@@
 The design of \GTT\ has the benefit of allowing a more appealing introduction rule for
-\IC{□} than Clouston et al.'s.
+box than Clouston et al.'s.
 
@@
 formalization. The full code is available at
-\url{https://github.com/niccoloveltri/agda-clott}. The formalization
-uses Agda 2.5.4.2 and Agda standard library 0.16. The paper is
-extracted from a literate Agda file, which implies that all the
-displayed code has passed Agda's type and termination checker.
+\url{https://github.com/niccoloveltri/agda-gtt}. The formalization
+uses Agda 2.5.4.2 and Agda standard library 0.16.
+\bibliographystyle{plain}
+\bibliography{literature}
 
-The material is organized in the following way.
-In \Cref{sec:prelim}, we discuss the metatheory and we give an
-overview of sized types.
-In \Cref{sec:syntax}, we introduce the syntax of \GTT, our object type theory for guarded recursion.
-Subsequently, we give a categorical semantics.
-In \Cref{sec:presheaf_sem}, we show how to implement presheaves over
-sizes and how to model the fragment of
-\GTT\ corresponding to simply typed lambda calculus.
-In \Cref{sec:guarded}, we discuss the semantics of the guarded
-recursive and coinductive features.
-In \Cref{sec:consistent}, we prove the object language sound \wrt the
-categorical model,
-%describe how to formally interpret the syntax into the model, 
-which in turn entails the consistency of the syntax.
-Finally, in \Cref{sec:concl}, we draw conclusions and suggest  future
-directions of work.
-
-%% give the Kripke semantics
-%%\GTT.
-%%For that, we first define a presheaf model and give the Kripke semantics, and then we show how to interpret the additional type and term formers of guarded recursive type theory.
-%%Finally, we conclude that the syntax is consistent in \Cref{sec:consistent}.
-
-%\NV{WIP from this point}
-
-%% To compare the strength of these two approaches, we develop denotational semantics of guarded recursive type theory in a type theory with sized types.
-%% This shows that guarded recursive type theory can be done via sized types.
-%% More specifically, we define a presheaf model of a simple type theory with guarded recursion \cite{BMSS-synthetic}.
-%% Simple types are interpreted via the usual presheaf semantics.
-
-%% In contrast, interpreting guarded recursion and guarded recursive types is more challenging.
-%% The most common model in the literature is the topos of trees \cite{BMSS-synthetic}.
-%% This is a presheaf topos, whose objects are sets indexed by a natural number.
-%% We use a slightly different approach: instead of natural numbers, we use sizes.
-%% This means that the required interpretations need to be modified.
-
-%% Our contributions are as follows
-
-%% In Section 2, we describe the meta-theory in which we work.
-%% In Section 3, we describe the syntax of the object theory, which is basically a variant of guarded recursion as done by Atkey and McBride \cite{atkey2013productive}.
-%% We do this in the form of a deep embedding.
-%% More specifically, we define data types representing the contexts, types, terms, and so on, and we give the rules for definitional equality.
-%% In Sections 4 and 5, we define the denotational semantics of this syntax.
-%% First, we give the interpretation of context, types, and terms in the model, and we show how to interpret simple type formers.
-%% Then we show this model supports guarded recursion and guarded recursive types.
-%% Finally, we show the syntax is consistent in Section 6.
-
-%% \subsection{Related Work}
-%% 
-%% Guarded recursion via the later modality was introduced by Nakano \NV{Citation}.
+\end{document}

### 2019-04-18 code-oneclock-paper/latex/Introduction.tex
url
started camera ready

@@
 a nameless analogue of Atkey and McBride's universal clock
-quantification. Clouston \etal \cite{CloustonBGB15} studied a
+quantification. Clouston \etal\ \cite{CloustonBGB15} studied a
 guarded variant of lambda calculus extended with a \IC{□} operation,
@@
 terminating definition of the semantic fixpoint combinator.
+
+The decision to restrict the clock context of \GTT\ to contain at 
+most one clock variable was dictated by 
+our choice to use Agda with sized types as the metatheory. In Agda, 
+it is possible to encode semantic clock contexts containing multiple 
+clocks as lists of sizes or as functions from a finite interval of 
+natural numbers into sizes. But Agda's support for sized types is 
+tailored to types depending on exactly one size, or on a finite but 
+precise number of sizes, which makes it cumbersome to work with types 
+depending on clock contexts containing an indefinite number of clocks. 
+More technically, as it was privately communicated to us by Agda 
+implementors, Agda's type inference only works properly for 
+first-order size contraints. We believe that if future Agda 
+releases will add the capability of handling multiple sizes, then it would 
+be possible to extend the semantics of \GTT\ to a model for the full 
+Atkey and McBride's type theory. We also believe that extending our 
+formalization to the multiclock case, while technically challenging, 
+will not be conceptually harder. 
+\GTT\ is stricly less expressive than Atkey and McBride's calculus, since we are 
+unable to implement nested coinductive types. But the one clock 
+variant of the calculus still allows the construction of a large 
+class of coinductive types and it is the subject of active research
+\cite{CloustonBGB15}.
 
@@
 formalization. The full code is available at
-\url{https://github.com/niccoloveltri/agda-clott}. The formalization
+\url{https://github.com/niccoloveltri/agda-gtt}. The formalization
 uses Agda 2.5.4.2 and Agda standard library 0.16. The paper is

### 2019-04-18 code-oneclock-paper/latex/paper.tex
started camera ready

@@
   Rasmus Ejlers M{\o}gelberg and Andrea Vezzosi for discussions and
-valuable hints.}%optional
+valuable hints. We thank the anonymous referees for their useful comments.}%optional
 
-%\nolinenumbers %uncomment to disable line numbering
+\nolinenumbers %uncomment to disable line numbering
 
@@
 
-%Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\EventEditors{John Q. Open and Joan R. Access}
-\EventNoEds{2}
-\EventLongTitle{42nd Conference on Very Important Topics (CVIT 2016)}
-\EventShortTitle{CVIT 2016}
-\EventAcronym{CVIT}
-\EventYear{2016}
-\EventDate{December 24--27, 2016}
-\EventLocation{Little Whinging, United Kingdom}
+%Editor-only macros:: begin (do not touch as
+%author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\EventEditors{Herman Geuvers}
+\EventNoEds{1}
+\EventLongTitle{4th International Conference on Formal Structures for Computation and Deduction (FSCD 2019)}
+\EventShortTitle{FSCD 2019}
+\EventAcronym{FSCD}
+\EventYear{2019}
+\EventDate{June 24--30, 2019}
+\EventLocation{Dortmund, Germany}
 \EventLogo{}
-\SeriesVolume{42}
-\ArticleNo{23}
+\SeriesVolume{131}
+\ArticleNo{33}
 
@@
 
-\subsection
-{Guarded Recursive Types}
+\subsection{Guarded Recursive Types}
 \label{sec:grt}
@@
 
-\section{Interpretation and Consistency}
+\section{Soundness and Consistency}
 \label{sec:consistent}
@@
 
+In \GTT\, we restrict the least fixpoint 
+operator \IC{μ} to act exclusively on strictly positive functors. This restriction is already 
+present in Atkey and McBride's calculus, which is aimed at 
+encoding coinductive types using the later modality and it does 
+not allow solving general guarded recursive domain equations.
+% such as\Ar{D} = ▻ \Ar{D → D}.
+\GTT\ is a variant of Atkey and McBride's type theory, therefore the
+similar restriction to stricly positive functors.  From the
+formalization perspective, this restriction allows us to use Agda's
+inductive types to model the guarded recursive types of GTT, as shown
+in Section \ref{sec:grt}. In future work, we plan to extend \GTT\ with
+the possibility of solving general guarded recursive domain
+equations. This could be done in two ways: extending the language with
+a universe, which allows the encoding of guarded recursive types as
+fixpoints in the universe as shown e.g. by M{\o}gelberg
+\cite{Mogelberg14}; or considering a \IC{μ} type former which, besides
+stricly positive functors, also operates on functors where all
+variables are guarded by an occurrence of the later modality. In the
+second option we have to consider strictly positive functors to encode
+usual inductive types, such as the natural numbers.
+
 Finally, we would like to understand whether sized types can be

### 2019-04-18 code-oneclock-paper/latex/Introduction.tex
Small fixes

@@
 need to be productive in the sense that every
-finite unfolding can be computed in a finite number of steps \cite{Coquand93}.
+finite part of the output can be computed in a finite number of steps \cite{Coquand93}.
 In Agda's encoding of coinductive types using ``musical notation''
@@
 by Abel and Chapman's work \cite{AC14}.
+There also are other approaches to sized types, one of those is developed by Sacchini
+\cite{Sacchini13}, but they allow less terms to be typed compared to Agda.
 
@@
 specification of guarded recursive types.
-These types can be used in combination with clock quantification to define  coinductive types \cite{atkey2013productive,bizjak2016guarded,BahrGM17}. Currently there is no
+These types can be used in combination with clock quantification to define  coinductive types \cite{atkey2013productive,BahrGM17,bizjak2016guarded}. Currently there is no
 implementation of a calculus for guarded recursion.
@@
 a nameless analogue of Atkey and McBride's universal clock
-quantification. Clouston \etal\ \cite{CloustonBGB15} studied a
+quantification. Clouston \etal \ \cite{CloustonBGB15} studied a
 guarded variant of lambda calculus extended with a \IC{□} operation,
@@
 model where the type formers of simply typed lambda calculus are
-evaluated using the standard Kripke semantics. Typically the semantics
-of type theories for guarded recursion is given in the topos of
+evaluated using the standard Kripke semantics. Typically, the semantics
+of a type theory for guarded recursion is given in the topos of
 trees or variations thereof \cite{BMSS-synthetic,MannaaM18,Mogelberg14}.
@@
 extracted from a literate Agda file, which implies that all the
-displayed code has passed Agda's type and termination checker.
+displayed code passed Agda's type and termination checker.
 

### 2019-04-18 code-oneclock-paper/latex/paper.tex
Small fixes

@@
   Coq traditionally employ strict syntactic productivity checks, which
-  commonly make programming with coinductive types convoluted.  One
+  often make programming with coinductive types convoluted.  One
   way to overcome this issue is by encoding productivity at the level
@@
 Since their definitions are standard, we do not discuss them in detail.
-For each of them, we need to make a case distinction based on the
-state of the clock context.
+For each of them, we need to make a case distinction based on the clock context.
 For example, the empty variable context \IC{•} is interpreted

### 2019-04-18 code-oneclock-paper/latex/Introduction.tex
Minor changes in intro

@@
 clocks as lists of sizes or as functions from a finite interval of 
-natural numbers into sizes. But Agda's support for sized types is 
+natural numbers into sizes. However, Agda's support for sized types is 
 tailored to types depending on exactly one size, or on a finite but 
@@
 implementors, Agda's type inference only works properly for 
-first-order size contraints. We believe that if future Agda 
-releases will add the capability of handling multiple sizes, then it would 
-be possible to extend the semantics of \GTT\ to a model for the full 
+first-order size constraints. We believe that if future Agda 
+releases add the capability of handling multiple sizes, it would 
+be possible to extend the semantics of \GTT\ to include the full 
 Atkey and McBride's type theory. We also believe that extending our 
 formalization to the multiclock case, while technically challenging, 
-will not be conceptually harder. 
+would not be conceptually harder.
+
 \GTT\ is stricly less expressive than Atkey and McBride's calculus, since we are 

### 2019-04-18 code-oneclock-paper/latex/Introduction.tex
later in the topos of trees

@@
 at the level of types: sized types and guarded recursion. A sized type
- is a type annotated with the number of unfolding that
+ is a type annotated with the number of unfoldings that
 elements of this type can undergo \cite{Hughes96}. Sized types have been implemented
@@
 There also are other approaches to sized types, one of those is developed by Sacchini
-\cite{Sacchini13}, but they allow less terms to be typed compared to Agda.
+\cite{Sacchini13}, but the latter allows less terms to be typed
+compared to Agda's approach.
 

### 2019-04-18 code-oneclock-paper/latex/Introduction.tex
Sacchini

@@
 by Abel and Chapman's work \cite{AC14}.
-There also are other approaches to sized types, one of those is developed by Sacchini
-\cite{Sacchini13}, but the latter allows less terms to be typed
+There also are other approaches to sized types.
+One of those is developed by Sacchini \cite{Sacchini13}, which allows less terms to be typed
 compared to Agda's approach.

### 2019-04-18 code-oneclock-paper/latex/Introduction.tex
more differences with Clouston et al

@@
 The design of \GTT\ has the benefit of allowing a more appealing introduction rule for
-\IC{□} than Clouston et al.'s.
+\IC{□} than Clouston \etal 's.
+\GTT\ also differs from Clouston \etal 's calculus in the class of definable
+guarded recursive types. We follow Atkey and McBride's approach and
+restrict the least fixpoint operator \IC{μ} to act on strictly positive
+functors, while Clouston \etal' \IC{μ} type former operates solely on functors
+in which all variables are guarded by an occurrence of the \IC{▻} modality.
 

### 2019-04-22 code-oneclock-paper/latex/Introduction.tex
Grammar fixes

--- 2019-04-18 code-oneclock-paper/latex/Introduction.tex
@@
 The design of \GTT\ has the benefit of allowing a more appealing introduction rule for
-\IC{□} than Clouston et al.'s.
+\IC{□} than Clouston \etal 's.
+\GTT\ also differs from Clouston \etal 's calculus in the class of definable
+guarded recursive types. We follow Atkey and McBride's approach and
+restrict the least fixpoint operator \IC{μ} to act on strictly positive
+functors, while \IC{μ} type former in Clouston \etal solely operates on functors
+in which all variables are guarded by an occurrence of the \IC{▻} modality.
 

### 2019-04-22 code-oneclock-paper/latex/paper.tex
started appendix
Work on appendix, added product
Grammar fixes

@@
 \usepackage{mathtools}
+\usepackage{proof}
+\usepackage{stmaryrd}
 
@@
 
-\input{Presheaves/Const}
+\input{Presheaves/Product}
+The weakening type former \IC{↑} of \GTT\ is modeled using the constant presheaf, which we denote by \AF{Const}.
 \input{Presheaves/Exp}
@@
 from the fact that sized types constitute a native feature of Agda, so
-we were able to fully develop our theory inside a proof assistent.
+we were able to fully develop our theory inside a proof assistant.
 
@@
 
+\input{Appendix}
+
 \end{document}

### 2019-04-30 code-oneclock-paper/types-abstract/abstract.tex
one clock motivation

@@
 
+The decision to restrict the clock context of \GTT\ to contain at most
+one clock variable was dictated by our choice to use Agda with sized
+types as the metatheory. In Agda, it is possible to encode semantic
+clock contexts containing multiple clocks as lists of sizes or as
+functions from a finite interval of natural numbers into
+sizes. However, Agda's support for sized types is tailored to types
+depending on exactly one size, or on a finite but precise number of
+sizes, which makes it cumbersome to work with types depending on clock
+contexts containing an indefinite number of clocks.
+
 Afterwards we develop a categorical semantics
